### 2024-11-26 paper/paper.qmd
reconstructed the data download script to with narrowed-down topic and wrote discussion point structure

---
title: "My title"
subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change/tree/main"
date: today
date-format: long
abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
format: pdf
number-sections: true
bibliography: references.bib
---

```{r}
#| include: false
#| warning: false
#| message: false

library(tidyverse)
library(palmerpenguins)
```

# Introduction

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....

# Data {#sec-data}

## Overview

We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...

Overview text

## Historical Background
- breifly introduces the necessary historical background for this analysis

## Measurement

- how population is recorded (not accurate count but by householad then estimates by average)
- why use population density instead of pure population #

## Outcome variables

Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.

Some of our data is of penguins (@fig-bills), from @palmerpenguins.

```{r}
#| label: fig-bills
#| fig-cap: Bills of penguins
#| echo: false

```

Talk more about it.

And also planes (@fig-planes). (You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)

```{r}
#| label: fig-planes
#| fig-cap: Relationship between wing length and width
#| echo: false
#| warning: false
#| message: false

```

Talk way more about it.

## Predictor variables

Add graphs, tables and text.

Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.

# Model

The goal of our modelling strategy is to evaluate the impact of 2 historical events in Shanghai during WWII.

Here we briefly describe the Difference-in-Difference analysis model used to investigate the impact of the Japanese forces taking over the Chinese district and International Settlement in November 1937 and December 1941 on population shift between different Districts in Shanghai.

Background details and diagnostics are included in [Appendix -@sec-model-details].

## Model set-up

Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.

\begin{align} 
y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
\mu_i &= \alpha + \beta_i + \gamma_i\\
\alpha &\sim \mbox{Normal}(0, 2.5) \\
\beta &\sim \mbox{Normal}(0, 2.5) \\
\gamma &\sim \mbox{Normal}(0, 2.5) \\
\sigma &\sim \mbox{Exponential}(1)
\end{align}

We run the model in R [@citeR] using the `rstanarm` package of @rstanarm. We use the default priors from `rstanarm`.

### Model justification

We expect a positive relationship between the size of the wings and time spent aloft. In particular...

We can use maths by including latex between dollar signs, for instance $\theta$.

# Results

Our results are summarized in @tbl-modelresults.

```{r}
#| echo: false
#| eval: true
#| warning: false
#| message: false

library(rstanarm)

first_model <-
  readRDS(file = here::here("models/first_model.rds"))
```

```{r}
#| echo: false
#| eval: true
#| label: tbl-modelresults
#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
#| warning: false

modelsummary::modelsummary(
  list(
    "First model" = first_model
  ),
  statistic = "mad",
  fmt = 2
)
```

# Discussion

## Reason why the French Concession was Exempted from Japanese Occupation
- During WWII, on the European battlefield, France surrendered to Germany on June 22nd of 1940 (Check this & reference with a credible source). Since Japan was on the same side as Germany during that time, Japanese armed forces decided allow the French Concession to retain its own governance.
- However, the French Concession is still constantly under the watch of the Japanese forces that has occupied the rest of Shanghai since 1942. 街上不得有侮辱日本的旗帜或者宣言，官方必须积极配合日本统治者进行有利于日本统治的宣传,etc.(can reference to video summary here)

## Refugees from outside of Shanghai Province
- industrialization was not so popular back in the 1930s, many provinces are still mostly rural. But warfare messed with the land and the yields, causing many farmers to starve and ultimately have to seek refugee (find job) in industrialized city (where income is not dependent on land yield)
- many people flooded to Shanghai for this reason (can insert calculation in data table 20 from reference book here)

## Job Oppurtunities
Aside from the instability caused by the Japanese armed forces, there are a few other reasons for Chinese population to move into the international settlement & French Concession.
1. Job opportunities
- Heart of Shanghai city in the 1930-1940s, high pop density lead to boom of economy = more job opportunities
- many factories are located with the settlements (less so in concession)

## Barrier to Entry in Job Market
2. Barrier to Entry for certain job types
- 旧时候 -- 通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。

## Weaknesses and next steps

### Data Measurement Weaknesses
- data was recorded during wartime, many numbers were missing
- base unit for population records is not ppl, it is instead "household". # of ppl in a household is estimated based on historical data
- many people chose to not report or partially report numbers due to convience or economic reasons, data may not be accurate

### Next Steps

\newpage

\appendix

# Appendix {-}

# Additional data details

# Model details {#sec-model-details}

## Posterior predictive check

In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...

In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...

```{r}
#| eval: true
#| echo: false
#| message: false
#| warning: false
#| label: fig-ppcheckandposteriorvsprior
#| layout-ncol: 2
#| fig-cap: "Examining how the model fits, and is affected by, the data"
#| fig-subcap: ["Posterior prediction check", "Comparing the posterior with the prior"]

pp_check(first_model) +
  theme_classic() +
  theme(legend.position = "bottom")

posterior_vs_prior(first_model) +
  theme_minimal() +
  scale_color_brewer(palette = "Set1") +
  theme(legend.position = "bottom") +
  coord_flip()
```

## Diagnostics

@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...

@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...

```{r}
#| echo: false
#| eval: true
#| message: false
#| warning: false
#| label: fig-stanareyouokay
#| fig-cap: "Checking the convergence of the MCMC algorithm"
#| fig-subcap: ["Trace plot", "Rhat plot"]
#| layout-ncol: 2

plot(first_model, "trace")

plot(first_model, "rhat")
```

\newpage

# References

### 2024-11-26 scripts/02-download_data.R

@@ -4,86 +4,41 @@
 # Date: 16 November 2024
 # Contact: jingying.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: Researched the data aspects necessary for the analysis and find relable sources
+# Pre-requisites: Researched the data aspects necessary for the analysis and find reliable sources
 # Data credibility is cross-referenced with scanned first-hand government written records in the 1930s-1940s
+# shanghai_pop_1852-1950 dataset is pulled from page 91-91 of the reference text 《旧上海人口变迁的研究》with the help of the LLM ChatGPT 4o (and manually adjusted)
+# PDF version of the reference text can be found in the other/literature section of the repository
 
 
 #### Workspace setup ####
 library(httr)
 library(readxl)
 library(arrow)
-library(fs)
 
 #### Download data ####
-
-# Define URLs and corresponding file names
-urls <- c(
-  "https://www.virtualshanghai.net/Asset/Source/dbData_ID-103_No-01.xlsx",
-  "https://www.virtualshanghai.net/Asset/Source/dbData_ID-101_No-01.xlsx",
-  "https://www.virtualshanghai.net/Asset/Source/dbData_ID-35_No-01.xls",
-  "https://www.virtualshanghai.net/Asset/Source/dbData_ID-94_No-01.xlsx",
-  "https://www.virtualshanghai.net/Asset/Source/dbData_ID-77_No-01.xlsx",
-  "https://www.virtualshanghai.net/Asset/Source/dbData_ID-153_No-01.xlsx",
-  "https://www.virtualshanghai.net/Asset/Source/dbData_ID-46_No-01.xlsx"
-)
-
-file_names <- c(
-  "1936_pop_density",
-  "1936_chn_pop",
-  "1937-44_settlements",
-  "1942_foreign_origin",
-  "1942_chn_origin",
-  "1942_pop_count_int",
-  "1941-43_pop"
-)
-
-# Define the output directory for Parquet files
+# Define output directory
 output_dir <- "data/01-raw_data"
-metadata_dir <- file.path(output_dir, "metadata")
-dir_create(metadata_dir)  # Create the metadata directory
 
-# Process each URL
-for (i in seq_along(urls)) {
-  # Download the file to a temporary location
-  temp_file <- tempfile(fileext = ifelse(grepl("\\.xls$", urls[i]), ".xls", ".xlsx"))
-  download.file(urls[i], destfile = temp_file, mode = "wb")
[…]

### 2024-11-26 scripts/03-clean_data.R

@@ -10,61 +10,42 @@
 #### Workspace setup ####
 library(tidyverse)
 library(arrow)
+library(dplyr)
 
 #### Read Raw Data ####
-# Define the main output directory and metadata subdirectory
-output_dir <- "data/01-raw_data"
-metadata_dir <- file.path(output_dir, "metadata")
-
-# Get a list of all Parquet files in the output directory and metadata subdirectory
-main_files <- list.files(output_dir, pattern = "\\.parquet$", full.names = TRUE)
-metadata_files <- list.files(metadata_dir, pattern = "\\.parquet$", full.names = TRUE)
-
-# Combine file lists
-all_files <- c(main_files, metadata_files)
-
-# Read each Parquet file and assign it to the environment with a clean name
-for (file in all_files) {
-  # Create a clean name for the data frame (remove directory and extension)
-  data_name <- tools::file_path_sans_ext(basename(file))
-  
-  # Read the Parquet file and assign it to the global environment
-  assign(data_name, read_parquet(file), envir = .GlobalEnv)
-  
-  message(paste("Loaded Parquet file:", file, "as", data_name))
-}
+pop_1852_1950 <- read_parquet(file.path("data/01-raw_data", "shanghai_population_1852_1950.parquet"))
+refugees_data <- read_parquet(file.path("data/01-raw_data", "refugees_data.parquet"))
 
 
 #### Clean data ####
-# Remember to remove datasheet without any observations!
+
+#### Clean the Refugees Data ####
+cleaned_refugees_data <- refugees_data |>
+  as.data.frame() |>
+  (\(df) df[, 1:6])() |>  # Keep only the first 6 columns
+  (\(df) df[, -c(2, 4)])() |>  # Remove columns 2 and 4
+  slice(-c(1:3)) |>  # Remove rows 1 to 3
+  setNames(c("date", "is_refugees", "fc_refugees", "total")) |>  # Rename columns
+  mutate(
+    date = as.Date(as.numeric(date), origin = "1899-12-30"),  # Convert Excel serial numbers
+  is_refugees = as.numeric(is_refugees), fc_refugees = as.numeric(fc_refugees)) |>
+  mutate(
+    across(c(is_refugees, fc_refugees, total), ~ replace_na(as.numeric(.), 0)) # treat NAs as 0
+  )
 
 
-cleaned_data <-
-  raw_data |>
-  janitor::clean_names() |>
-  select(wing_width_mm, wing_length_mm, flying_time_sec_first_timer) |>
[…]

### 2024-11-26 paper/paper.qmd
setup basic structure for Data section & added content points to discussion

@@
   - Sandy Yu
-thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change/tree/main"
+thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
 date: today
@@
 
-Overview text
+## Data Sources
+- talk about where the data in my primary reference book is gathered
+- mentions the credibility of source and unstability of recording instrument & methodology
 
 ## Historical Background
-- breifly introduces the necessary historical background for this analysis
+Place: Shanghai, China
+When: 1936-1942
+Who: Chinese population in Shanghai
+
+Define:
+1. give 1-2 sentence broad overview of China's state of unrest
+2.THREE districts in Shanghai: Chinese District, International Settlement, French Concession
+- who controlled each district and the level of governance each authority have in comparison to Chinese government
+3.Outline area (%) of each district (do not get into specifics, put that in Results section)
+
+Important Event Timeline
+1. 1937-08-13: Japanese armed forces entered Shanghai
+2. 1937-11-12: Japanese armed forces claims occupation of Shanghai --> ends Chinese district 
+3. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)
+4. 1945-08-15: Japan surrendered in WWII
+5. 1945-10: most Japanese armed forces withdrawed from Shanghai
 
@@
 - why use population density instead of pure population #
+- how year variables correspond to the timeline (ex. if an event occured in Nov of 1937, would I take valeus of 1937 as a variable for prior to event occurance or after?)
 
 ## Outcome variables
+- outcome variable is "population change in International Settlement during 1937-1942" measured in population density
 
 Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-
 Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
-#| label: fig-bills
-#| fig-cap: Bills of penguins
-#| echo: false
-
-```
-
-Talk more about it.
-
-And also planes (@fig-planes).
-(You can change the height and width, but don't worry about doing that until you have finished every other aspect of the paper - Quarto will try to make it look nice and the defaults usually work well once you have enough text.)
 
@@
 
-Talk way more about it.
-
 ## Predictor variables
 
-Add graphs, tables and text.
+- most important predictors include time sensitive indicators: Event1 & Event2
 
-Use sub-sub-headings for each outcome variable and feel free to combine a few into one if they go together naturally.
+Event1: indicator variable for 1937 (1 if year >= 1937 & <= 1941, 0 otherwise)
+- mention a bit about the measurement
+
+Event2: indicator variable for 1937 (1 if year >= 1941, 0 otherwise)
+- mention a bit about the measurement
 
@@
 
-## Job Oppurtunities
+### Job Oppurtunities in Shanghai
 Aside from the instability caused by the Japanese armed forces, there are a few other reasons for Chinese population to move into the international settlement & French Concession.
@@
 
-## Barrier to Entry in Job Market
+### Barrier to Entry in Job Market
 2. Barrier to Entry for certain job types
 - 旧时候 -- 通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。
+
+## Instability after Japanese Occupation ends in WWII: Chinese Civil War
+- after the Japanese armed forces withdrawed from Shanghai, what follows is not recovery and rest for the local population
+- Competition for power within China's 2 political parties caused full-scale political warfare, now known as the *Chinese Civil War*
+- unlike Western political parties, Chinese political parties in the 1900s are more like parties of a throne.
+They each have their own ideology and an armed forces that follow.
+Most of all of the provinces are effected by this internal warfare, which ended in 1949 as 国民党 lost and withdrawed to Taiwan.
 

### 2024-11-26 scripts/03-clean_data.R

@@ -45,7 +45,11 @@ cleaned_refugees_data <- refugees_data |>
 #  ) |>
 #  ungroup()
 
+#### Clean the Population 1852-1950 Data ####
+
+
+
 
 
 #### Save data ####
-write_csv(cleaned_data, "outputs/data/analysis_data.csv")
+write_parquet(cleaned_pop_1852_1950, "data/02-analysis_data/pop_analysis_data.parquet")

### 2024-11-27 scripts/00-simulate_data.R
finished data simulation script and corresponding tests

@@ -1,52 +1,62 @@
 #### Preamble ####
-# Purpose: Simulates a dataset of Australian electoral divisions, including the 
-  #state and party that won each division.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Simulates a dataset to fit into DiD model that evaluates the population between within districts in Shanghai between 1936-1942
+# Author: Sandy Yu
+# Date: 16 November 2024
+# Contact: jingying.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` package must be installed
+# Pre-requisites: The `tidyverse` and `dplyr` packages must be installed
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
-set.seed(853)
+library(dplyr)
+
 
 
 #### Simulate data ####
-# State names
-states <- c(
-  "New South Wales",
-  "Victoria",
-  "Queensland",
-  "South Australia",
-  "Western Australia",
-  "Tasmania",
-  "Northern Territory",
-  "Australian Capital Territory"
-)
+set.seed(21)
 
-# Political parties
-parties <- c("Labor", "Liberal", "Greens", "National", "Other")
+# Define years and districts
+years <- 1936:1942
+districts <- c("Chinese District", "International Settlement", "French Concession")
 
-# Create a dataset by randomly assigning states and parties to divisions
-analysis_data <- tibble(
-  division = paste("Division", 1:151),  # Add "Division" to make it a character
-  state = sample(
-    states,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.25, 0.25, 0.15, 0.1, 0.1, 0.1, 0.025, 0.025) # Rough state population distribution
-  ),
-  party = sample(
-    parties,
-    size = 151,
-    replace = TRUE,
-    prob = c(0.40, 0.40, 0.05, 0.1, 0.05) # Rough party distribution
+# Create a data frame for all combinations of year and district
+simulated_data <- expand.grid(Year = years, District = districts)
+
+# Assign base population for 1936
+simulated_data <- simulated_data %>%
+  mutate(
+    Base_Population = case_when(
+      District == "Chinese District" ~ 3000000,  # Base for CD
+      District == "International Settlement" ~ 1500000,  # Base for IS
[…]

### 2024-11-27 scripts/01-test_simulated_data.R

@@ -1,89 +1,108 @@
 #### Preamble ####
-# Purpose: Tests the structure and validity of the simulated Australian 
-  #electoral divisions dataset.
-# Author: Rohan Alexander
-# Date: 26 September 2024
-# Contact: rohan.alexander@utoronto.ca
+# Purpose: Tests the structure and validity of the simulated simulated_data
+# Author: Sandy Yu
+# Date: 16 November 2024
+# Contact: jingying.yu@mail.utoronto.ca
 # License: MIT
 # Pre-requisites: 
   # - The `tidyverse` package must be installed and loaded
   # - 00-simulate_data.R must have been run
-# Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
+library(arrow)
 
-analysis_data <- read_csv("data/00-simulated_data/simulated_data.csv")
+simulated_data <- read_parquet("data/00-simulated_data/simulated_data.parquet")
 
 # Test if the data was successfully loaded
-if (exists("analysis_data")) {
-  message("Test Passed: The dataset was successfully loaded.")
+if (exists("simulated_data")) {
+  message("Test Passed: The simulated_data was successfully loaded.")
 } else {
-  stop("Test Failed: The dataset could not be loaded.")
+  stop("Test Failed: The simulated_data could not be loaded.")
 }
 
 
 #### Test data ####
-
-# Check if the dataset has 151 rows
-if (nrow(analysis_data) == 151) {
-  message("Test Passed: The dataset has 151 rows.")
+# Test 1: Check if the simulated_data has the correct number of rows
+expected_rows <- length(years) * length(districts)
+if (nrow(simulated_data) == expected_rows) {
+  message("Test Passed: The simulated_data has the correct number of rows.")
 } else {
-  stop("Test Failed: The dataset does not have 151 rows.")
+  stop("Test Failed: The simulated_data does not have the correct number of rows.")
 }
 
-# Check if the dataset has 3 columns
-if (ncol(analysis_data) == 3) {
-  message("Test Passed: The dataset has 3 columns.")
+# Test 2: Check if the simulated_data has the correct number of columns
+expected_columns <- 10  # Adjust based on the simulated_data structure
+if (ncol(simulated_data) == expected_columns) {
+  message("Test Passed: The simulated_data has the correct number of columns.")
 } else {
-  stop("Test Failed: The dataset does not have 3 columns.")
+  stop("Test Failed: The simulated_data does not have the correct number of columns.")
 }
 
[…]

### 2024-11-27 scripts/03-clean_data.R

@@ -52,4 +52,4 @@ cleaned_refugees_data <- refugees_data |>
 
 
 #### Save data ####
-write_parquet(cleaned_pop_1852_1950, "data/02-analysis_data/pop_analysis_data.parquet")
+write_parquet(pop_1852_1950, "data/02-analysis_data/pop_analysis_data.parquet")

### 2024-11-28 scripts/00-simulate_data.R
filled in missing values for primary dataset using cleaned values from different dataset, data cleaning is complete

@@ -4,14 +4,14 @@
 # Date: 16 November 2024
 # Contact: jingying.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: The `tidyverse` and `dplyr` packages must be installed
+# Pre-requisites: The `tidyverse`, `dplyr`, and `arrow` packages must be installed
 # Any other information needed? Make sure you are in the `starter_folder` rproj
 
 
 #### Workspace setup ####
 library(tidyverse)
 library(dplyr)
-
+library(arrow)
 
 
 #### Simulate data ####
@@ -22,10 +22,10 @@ years <- 1936:1942
 districts <- c("Chinese District", "International Settlement", "French Concession")
 
 # Create a data frame for all combinations of year and district
-simulated_data <- expand.grid(Year = years, District = districts)
+simulated_data <- expand.grid(year = years, District = districts)
 
 # Assign base population for 1936
-simulated_data <- simulated_data %>%
+simulated_data <- simulated_data |>
   mutate(
     Base_Population = case_when(
       District == "Chinese District" ~ 3000000,  # Base for CD
@@ -35,23 +35,24 @@ simulated_data <- simulated_data %>%
   )
 
 # Add the effects of events with corrected is_occupied
-simulated_data <- simulated_data %>%
+simulated_data <- simulated_data |>
   mutate(
-    cd_occupied = ifelse(Year >= 1937, 1, 0),  # Event 1: 1937 Japanese occupation of CD
-    french_surrender = ifelse(Year >= 1940, 1, 0),  # Event 2: 1940 rejection of refugees in FC
-    is_occupied = ifelse(Year >= 1942, 1, 0),   # Event 3: 1942 Japanese occupation of IS
+    cd_occupied = ifelse(year >= 1937, 1, 0),  # Event 1: 1937 Japanese occupation of CD
+    french_surrender = ifelse(year >= 1940, 1, 0),  # Event 2: 1940 rejection of refugees in FC
+    is_occupied = ifelse(year >= 1942, 1, 0),   # Event 3: 1942 Japanese occupation of IS
     Population_Change = case_when(
-      District == "Chinese District" & cd_occupied == 1 ~ -500000 * (Year - 1936), # CD population declines after 1937
-      District == "International Settlement" & cd_occupied == 1 ~ 200000 * (Year - 1936), # IS increases due to refugees
-      District == "French Concession" & cd_occupied == 1 & french_surrender == 0 ~ 100000 * (Year - 1936), # FC increases until 1940
[…]

### 2024-11-28 scripts/02-download_data.R

@@ -23,9 +23,10 @@ output_dir <- "data/01-raw_data"
 refugee_xls_file <- file.path(output_dir, "refugees_data.xls")  # Refugee .xls file
 refugee_parquet_file <- file.path(output_dir, "refugees_data.parquet")  # Refugee Parquet file
 
-# File paths for the population data
-population_xlsx_file <- file.path(output_dir, "shanghai_population_1852_1950.xlsx")  # Population .xlsx file
-population_parquet_file <- file.path(output_dir, "shanghai_population_1852_1950.parquet")  # Population Parquet file
+
+# File paths for the 1941-42 data
+data_1941_42_xlsx_file <- file.path(output_dir, "1941_42.xlsx")  # 1941-42 .xlsx file
+data_1941_42_parquet_file <- file.path(output_dir, "1941_42.parquet")  # 1941-42 Parquet file
 
 #### Download and Process Refugee Data ####
 # Download the refugee data
@@ -36,9 +37,23 @@ download.file(url = "https://www.virtualshanghai.net/Asset/Source/dbData_ID-35_N
 # Read only the first sheet ("Data") from the refugee data
 refugees_data <- read_excel(refugee_xls_file, sheet = "Data")
 
+
+#### Download and Process 1941-42 Data ####
+# Download the 1941-42 data
+download.file(url = "https://www.virtualshanghai.net/Asset/Source/dbData_ID-46_No-01.xlsx",
+              destfile = data_1941_42_xlsx_file,
+              mode = "wb")
+
+# Read the second sheet ("Data") from the 1941-42 data
+data_1941_42 <- read_excel(data_1941_42_xlsx_file, sheet = "Data")
+
+
 #### Save data ####
 write_parquet(refugees_data, sink = refugee_parquet_file)
 unlink(refugee_xls_file)
 
-population_data <- read_excel(population_xlsx_file)
-write_parquet(population_data, sink = population_parquet_file)
+population_data <- read_excel("data/01-raw_data/shanghai_population_1852_1950.xlsx")
+write_parquet(population_data, "data/01-raw_data/shanghai_population_1852_1950.parquet")
+
+write_parquet(data_1941_42, sink = data_1941_42_parquet_file)
+unlink(data_1941_42_xlsx_file)  # Delete the temporary .xlsx file

### 2024-11-28 scripts/03-clean_data.R

@@ -15,6 +15,7 @@ library(dplyr)
 #### Read Raw Data ####
 pop_1852_1950 <- read_parquet(file.path("data/01-raw_data", "shanghai_population_1852_1950.parquet"))
 refugees_data <- read_parquet(file.path("data/01-raw_data", "refugees_data.parquet"))
+pop_1941_42 <- read_parquet(file.path("data/01-raw_data", "1941_42.parquet"))
 
 
 #### Clean data ####
@@ -34,22 +35,168 @@ cleaned_refugees_data <- refugees_data |>
   )
 
 
-#year_refugee_summary <- cleaned_refugees_data |>
-#  group_by(date = as.numeric(format(date, "%Y"))) |>  # Group by year extracted from the `date` column
-#  summarize(
-#    total_is_refugees = sum(is_refugees, na.rm = TRUE),   # Summing `is_refugees`
-#    total_fc_refugees = sum(fc_refugees, na.rm = TRUE)    # Summing `fc_refugees`
-#  ) |>
-#  mutate(
-#    total_sum = total_is_refugees + total_fc_refugees     # Calculate the total column
-#  ) |>
-#  ungroup()
+
+# Get a year end summary for refugges within each district
+# Ensure 'date' column is in Date format
+year_refugees_data <- cleaned_refugees_data |>
+  mutate(date = as.Date(date))
+
+# Manually select rows for 'is_refugees' and 'fc_refugees'
+
+
+manual_is_refugees <- year_refugees_data %>%
+  filter(date %in% as.Date(c("1937-12-14", "1938-12-29", "1939-10-04", 
+                             "1940-12-18", "1941-08-15", "1942-10-01"))) %>%
+  mutate(year = format(date, "%Y")) %>%
+  select(date, year, is_refugees)
+
+manual_fc_refugees <- year_refugees_data %>%
+  filter(date %in% as.Date(c("1937-12-14", "1938-10-23", "1939-06-20", 
+                             "1940-12-18", "1941-08-15", "1942-10-01"))) %>%
+  mutate(year = format(date, "%Y")) %>%
+  select(date, year, fc_refugees)
+
+
+# Combine the manually selected data
+year_refugee_summary <- manual_is_refugees |>
+  left_join(manual_fc_refugees, by = "year")
+
+# Keep only year, is_refugees, and fc_refugees
+year_refugee_summary <- year_refugee_summary |>
+  select(year, is_refugees, fc_refugees)
+
+
 
[…]

### 2024-11-28 scripts/03-clean_data.R
saved a new intermediate dataset that can be used in paper

@@ -198,5 +198,6 @@ combined_data <- rbind(
 #### Save data ####
 write_parquet(pop_1852_1950, "data/02-analysis_data/pop_analysis_data.parquet")
 write_parquet(cleaned_refugees_data, "data/02-analysis_data/cleaned_refugees_data.parquet")
+write_parquet(calibration_percent, "data/02-analysis_data/calibration_percent.parquet")
 write_parquet(combined_data, "data/02-analysis_data/combined_data.parquet")
 

### 2024-11-28 paper/paper.qmd
finished model construction

@@
 
+\[
+Population_{it} = \beta_0 + \beta_1 \cdot cd\_occupied_t + \beta_2 \cdot french\_surrender_t + \beta_3 \cdot is\_occupied_t + \beta_4 \cdot DistrictType_i + \beta_5 \cdot (cd\_occupied_t \times DistrictType_i) + \beta_6 \cdot (french\_surrender_t \times DistrictType_i) + \beta_7\cdot (is\_occupied_t \times DistrictType_i) + \epsilon{it}
+\]
 ### Model justification
@@
 
-first_model <-
-  readRDS(file = here::here("models/first_model.rds"))
+did_model <-
+  readRDS(file = here::here("models/did_model.rds"))
 ```
@@
   list(
-    "First model" = first_model
+    "Population model" = did_model
   ),

### 2024-11-28 scripts/03-clean_data.R

@@ -195,9 +195,32 @@ combined_data <- rbind(
   combined_data[6, ]  # Keep rows after 1939
 )
 
+
+# Reshape the final combined_data into model-friendly format
+model_format <- combined_data |>
+  pivot_longer(
+    cols = c(chn_admin_pop, is_pop, fc_pop),
+    names_to = "district_type",
+    values_to = "population"
+  ) |>
+  mutate(
+    # Create a categorical variable for district type
+    district_type = case_when(
+      district_type == "chn_admin_pop" ~ "Chinese-administered area",
+      district_type == "is_pop" ~ "International Settlement",
+      district_type == "fc_pop" ~ "French Concession")) |> 
+  mutate(cd_occupied = ifelse(year >= 1937, 1, 0),  # Event 1: Japanese occupation of CD
+         french_surrender = ifelse(year >= 1940, 1, 0),  # Event 2: Rejection of refugees in FC
+         is_occupied = ifelse(year >= 1942, 1, 0)) |> # Event 3: Japanese occupation of IS
+  mutate(district_is = ifelse(district_type == "International Settlement", 1, 0),  # Dummy for IS
+         district_fc = ifelse(district_type == "French Concession", 1, 0)) |>         # Dummy for FC
+  mutate(district_type = as.factor(district_type))  # Ensure District is a factor
+
+
 #### Save data ####
 write_parquet(pop_1852_1950, "data/02-analysis_data/pop_analysis_data.parquet")
 write_parquet(cleaned_refugees_data, "data/02-analysis_data/cleaned_refugees_data.parquet")
 write_parquet(calibration_percent, "data/02-analysis_data/calibration_percent.parquet")
 write_parquet(combined_data, "data/02-analysis_data/combined_data.parquet")
-
+write_parquet(model_format, "data/02-analysis_data/model_format.parquet")
+write_csv(model_format, "data/02-analysis_data/model_format.csv")

### 2024-11-29 scripts/00-simulate_data.R
added saving command to model script

@@ -61,3 +61,4 @@ simulated_data <- simulated_data |>
 
 #### Save data ####
 write_parquet(simulated_data, "data/00-simulated_data/simulated_data.parquet")
+write_csv(simulated_data, "data/00-simulated_data/simulated_data.csv")

### 2024-11-29 scripts/06-model_data.R

@@ -11,27 +11,29 @@
 #### Workspace setup ####
 library(tidyverse)
 library(rstanarm)
+library(arrow)
 
 #### Read data ####
-analysis_data <- read_csv("data/analysis_data/analysis_data.csv")
+model_format <- read_parquet("data/02-analysis_data/model_format.parquet")
 
 ### Model data ####
-first_model <-
-  stan_glm(
-    formula = flying_time ~ length + width,
-    data = analysis_data,
-    family = gaussian(),
-    prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_intercept = normal(location = 0, scale = 2.5, autoscale = TRUE),
-    prior_aux = exponential(rate = 1, autoscale = TRUE),
-    seed = 853
-  )
+
+did_model <- stan_glm(
+  population ~ cd_occupied * district_type + 
+    french_surrender * district_type + 
+    is_occupied * district_type,
+  data = model_format,
+  family = gaussian(),  # Continuous dependent variable
+  prior = normal(0, 10),  # Weakly informative prior
+  prior_intercept = normal(0, 10),
+  chains = 4, iter = 2000, seed = 123
+)
 
 
 #### Save model ####
 saveRDS(
-  first_model,
-  file = "models/first_model.rds"
+  did_model,
+  file = "models/did_model.rds"
 )
 
 

### 2024-11-29 scripts/04-test_analysis_data.R
finished analysis data testing script

@@ -9,61 +9,181 @@
 
 
 #### Workspace setup ####
+model_format <- read_parquet("data/02-analysis_data/model_format.parquet")
+year_refugee_summary <- read_parquet("data/02-analysis_data/year_refugee_summary.parquet")
+calibration_percent <- read_parquet("data/02-analysis_data/calibration_percent.parquet")
+
 library(tidyverse)
 library(testthat)
-
-data <- read_csv("data/02-analysis_data/analysis_data.csv")
-
+library(arrow)
 
 #### Test data ####
-# Test that the dataset has 151 rows - there are 151 divisions in Australia
-test_that("dataset has 151 rows", {
-  expect_equal(nrow(analysis_data), 151)
+
+## Basic Tests
+test_that("year column contains only values from 1936 to 1942", {
+  expect_true(all(model_format$year >= 1936 & model_format$year <= 1942))
 })
 
-# Test that the dataset has 3 columns
-test_that("dataset has 3 columns", {
-  expect_equal(ncol(analysis_data), 3)
+test_that("there are no missing values in the dataset", {
+  expect_true(all(complete.cases(model_format)))
 })
 
-# Test that the 'division' column is character type
-test_that("'division' is character", {
-  expect_type(analysis_data$division, "character")
+test_that("district_type has only three unique values and each appears the same amount of times", {
+  unique_districts <- unique(model_format$district_type)
+  expect_length(unique_districts, 3)
+  
+  # Check that each district appears the same number of times
+  district_counts <- table(model_format$district_type)
+  expect_true(all(district_counts == district_counts[1]))
 })
 
-# Test that the 'party' column is character type
-test_that("'party' is character", {
-  expect_type(analysis_data$party, "character")
+
+test_that("class type for each column is appropriate", {
+  expect_type(model_format$year, "double")
+  expect_type(model_format$district_type, "character")
+  expect_type(model_format$population, "double")
+  expect_type(model_format$cd_occupied, "double")
+  expect_type(model_format$french_surrender, "double")
+  expect_type(model_format$is_occupied, "double")
 })
 
-# Test that the 'state' column is character type
-test_that("'state' is character", {
-  expect_type(analysis_data$state, "character")
+
+
+## Test that missing value in initial model_format dataset has been calibrated correctly with the help of other datasets
+# Test for 1938: Chinese-administered area
[…]

### 2024-12-01 paper/paper.qmd
updated model section in paper.qmd

--- 2024-11-26 paper/paper.qmd
@@
 library(tidyverse)
-library(palmerpenguins)
+library(arrow)
+library(knitr)
+library(modelsummary)
+library(rstanarm)
 ```
@@
 ## Data Sources
+
 -   talk about where the data in my primary reference book is gathered
@@
 ## Historical Background
-Place: Shanghai, China
-When: 1936-1942
-Who: Chinese population in Shanghai
 
-Define:
-1. give 1-2 sentence broad overview of China's state of unrest
-2.THREE districts in Shanghai: Chinese District, International Settlement, French Concession
-- who controlled each district and the level of governance each authority have in comparison to Chinese government
-3.Outline area (%) of each district (do not get into specifics, put that in Results section)
+Place: Shanghai, China When: 1936-1942 Who: Chinese population in Shanghai
 
-Important Event Timeline
-1. 1937-08-13: Japanese armed forces entered Shanghai
-2. 1937-11-12: Japanese armed forces claims occupation of Shanghai --> ends Chinese district 
-3. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)
-4. 1945-08-15: Japan surrendered in WWII
-5. 1945-10: most Japanese armed forces withdrawed from Shanghai
+Define: 1.
+give 1-2 sentence broad overview of China's state of unrest 2.THREE districts in Shanghai: Chinese District, International Settlement, French Concession - who controlled each district and the level of governance each authority have in comparison to Chinese government 3.Outline area (%) of each district (do not get into specifics, put that in Results section)
+
+Important Event Timeline 1.
+1937-08-13: Japanese armed forces entered Shanghai 2.
+1937-11-12: Japanese armed forces claims occupation of Shanghai --\> ends Chinese district 3.
+1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date) 4.
+1945-08-15: Japan surrendered in WWII 5.
+1945-10: most Japanese armed forces withdrawed from Shanghai
 
@@
 -   how population is recorded (not accurate count but by householad then estimates by average)
-- why use population density instead of pure population #
+-   why use population density instead of pure population \#
 -   how year variables correspond to the timeline (ex. if an event occured in Nov of 1937, would I take valeus of 1937 as a variable for prior to event occurance or after?)
@@
 ## Outcome variables
+
 -   outcome variable is "population change in International Settlement during 1937-1942" measured in population density
 
-Add graphs, tables and text. Use sub-sub-headings for each outcome variable or update the subheading to be singular.
-Some of our data is of penguins (@fig-bills), from @palmerpenguins.
-
-```{r}
+```{r, include = FALSE}
 #| label: fig-planes
@@
 
-Event1: indicator variable for 1937 (1 if year >= 1937 & <= 1941, 0 otherwise)
-- mention a bit about the measurement
+Event1: indicator variable for 1937 (1 if year \>= 1937 & \<= 1941, 0 otherwise) - mention a bit about the measurement
 
-Event2: indicator variable for 1937 (1 if year >= 1941, 0 otherwise)
-- mention a bit about the measurement
+Event2: indicator variable for 1937 (1 if year \>= 1941, 0 otherwise) - mention a bit about the measurement
 
@@
 
-Define $y_i$ as the number of seconds that the plane remained aloft. Then $\beta_i$ is the wing width and $\gamma_i$ is the wing length, both measured in millimeters.
+$$y_{it}|\mu_{it}, \sigma \sim \mbox{Normal}(\mu_{it}, \sigma)$$
 
-\begin{align} 
-y_i|\mu_i, \sigma &\sim \mbox{Normal}(\mu_i, \sigma) \\
-\mu_i &= \alpha + \beta_i + \gamma_i\\
-\alpha &\sim \mbox{Normal}(0, 2.5) \\
-\beta &\sim \mbox{Normal}(0, 2.5) \\
-\gamma &\sim \mbox{Normal}(0, 2.5) \\
-\sigma &\sim \mbox{Exponential}(1)
-\end{align}
+$$\mu_{it} = \alpha + \beta_1 \cdot \mbox{cd_occupied}_{it} + \beta_2 \cdot \mbox{french_surrender}_{it} + \beta_3 \cdot \mbox{is_occupied}_{it} + \beta_4 \cdot \mbox{district_type}_{i, IS} +
+\\
+\beta_5 \cdot \mbox{district_type}_{i, FC} + \beta_6 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + 
+\\
+\beta_7 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, FC} + \beta_8 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, IS} + 
+\\
+\beta_9 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, FC} + 
+\\
+\beta_{10} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + \beta_{11} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, FC}$$
+
+$$\alpha \sim \mbox{Normal}(0, 2.5)$$
+
+$$\beta_k \sim \mbox{Normal}(0, 2.5) \quad \mbox{for } k = 1, ..., 11$$
+
+$$\sigma \sim \mbox{Exponential}(1)$$
+
+**Where**:
+
+-   $y_{i,t}$: Observed population in district i at year t.
+-   $\mbox{cd_occupied}_{i,t}$: Indicator for whether the Chinese-administered district was occupied by Japanese forces in year t (1 if $t \geq 1937$, 0 otherwise).
+-   $\mbox{french_surrender}_{i,t}$: Indicator for the French Surrendering to Germany in 1940, leading to the French Concession rejecting refugees in Shanghai (1 if $t \geq 1940$, 0 otherwise).
+-   $\mbox{is_occupied}_{i,t}$: Indicator for the Japanese occupation of the International Settlement in 1942 (1 if $t \geq 1942$, 0 otherwise).
+-   $\mbox{district_type}_{i, IS}$: Dummy variable for International Settlement districts (1 if i is IS, 0 otherwise).
+-   $\mbox{district_type}_{i, FC}$: Dummy variable for French Concession districts (1 if i is FC, 0 otherwise).
+
+**Interaction Terms**:
+The interaction terms in the model are essential because they capture how the impact of historical events (e.g., the 1937 occupation of Chinese-administered districts, the 1940 refugee rejection in the French Concession, and the 1942 occupation of the International Settlement) varies across different district types.
+By including interactions between event indicators and district types, the model accounts for district-specific responses to each event, controlling for the fact that the effect of an event on population changes may not be uniform across all districts.
+For instance, the 1937 occupation might lead to population declines in Chinese-administered districts but population increases in the International Settlement due to refugee influx.
+These terms ensure that the model can differentiate and estimate the unique effects of each event within each district type, thereby improving precision and interpretability.
+
+-   $\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}$: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
+-   $\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}$: Captures the effect of the 1937 occupation on the French Concession in comparison to the base district.
+-   $\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, IS}$: Effect of the 1940 refugee rejection on the International Settlement.
+-   $\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, FC}$: Effect of the 1940 refugee rejection on the French Concession.
+-   $\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}$: Effect of the 1942 occupation on the International Settlement.
+-   $\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}$: Effect of the 1942 occupation on the French Concession.
 
@@
   list(
-    "First model" = first_model
+    "Population model" = did_model
   ),
   statistic = "mad",
-  fmt = 2
+  fmt = 2,
+  metrics = c("R2", "RMSE")
 )
@@
 ## Reason why the French Concession was Exempted from Japanese Occupation
+
 -   During WWII, on the European battlefield, France surrendered to Germany on June 22nd of 1940 (Check this & reference with a credible source).
@@
 ## Refugees from outside of Shanghai Province
+
 -   industrialization was not so popular back in the 1930s, many provinces are still mostly rural.
@@
 ### Job Oppurtunities in Shanghai
+
 Aside from the instability caused by the Japanese armed forces, there are a few other reasons for Chinese population to move into the international settlement & French Concession.
-1. Job opportunities
-- Heart of Shanghai city in the 1930-1940s, high pop density lead to boom of economy = more job opportunities
-- many factories are located with the settlements (less so in concession)
+1.
+Job opportunities - Heart of Shanghai city in the 1930-1940s, high pop density lead to boom of economy = more job opportunities - many factories are located with the settlements (less so in concession)
 
 ### Barrier to Entry in Job Market
+
 2.  Barrier to Entry for certain job types
+
 -   旧时候 -- 通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。
@@
 ## Instability after Japanese Occupation ends in WWII: Chinese Civil War
+
 -   after the Japanese armed forces withdrawed from Shanghai, what follows is not recovery and rest for the local population
@@
 ### Data Measurement Weaknesses
+
 -   data was recorded during wartime, many numbers were missing
-- base unit for population records is not ppl, it is instead "household". # of ppl in a household is estimated based on historical data
+-   base unit for population records is not ppl, it is instead "household". \# of ppl in a household is estimated based on historical data
 -   many people chose to not report or partially report numbers due to convience or economic reasons, data may not be accurate
@@
 
-# Appendix {-}
+# Appendix {.unnumbered}
 
@@
 
-pp_check(first_model) +
+model_format <- read_parquet(file = here::here("data/02-analysis_data/model_format.parquet"))
+
+pp_check(did_model) +
   theme_classic() +
@@
 
-posterior_vs_prior(first_model) +
+posterior_vs_prior(did_model) +
   theme_minimal() +
@@
 
-plot(first_model, "trace")
+plot(did_model, "trace")
 
-plot(first_model, "rhat")
+plot(did_model, "rhat")
 ```

### 2024-12-01 paper/paper.tex
updated model section in paper.qmd

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
\PassOptionsToPackage{dvipsnames,svgnames,x11names}{xcolor}
%
\documentclass[
  letterpaper,
  DIV=11,
  numbers=noendperiod]{scrartcl}

\usepackage{amsmath,amssymb}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
\usepackage{lmodern}
\ifPDFTeX\else  
    % xetex/luatex font selection
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\setlength{\emergencystretch}{3em} % prevent overfull lines
\setcounter{secnumdepth}{5}
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
% Correct order of tables after \paragraph or \subparagraph
\usepackage{etoolbox}
\makeatletter
\patchcmd\longtable{\par}{\if@noskipsec\mbox{}\fi\par}{}{}
\makeatother
% Allow footnotes in longtable head/foot
\IfFileExists{footnotehyper.sty}{\usepackage{footnotehyper}}{\usepackage{footnote}}
\makesavenoteenv{longtable}
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

\usepackage{float}
\usepackage{tabularray}
\usepackage[normalem]{ulem}
\usepackage{graphicx}
\UseTblrLibrary{booktabs}
\UseTblrLibrary{siunitx}
\NewTableCommand{\tinytableDefineColor}[3]{\definecolor{#1}{#2}{#3}}
\newcommand{\tinytableTabularrayUnderline}[1]{\underline{#1}}
\newcommand{\tinytableTabularrayStrikeout}[1]{\sout{#1}}
\KOMAoption{captions}{tableheading}
\makeatletter
\makeatother
\makeatletter
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\AtBeginDocument{%
\ifdefined\contentsname
  \renewcommand*\contentsname{Table of contents}
\else
  \newcommand\contentsname{Table of contents}
\fi
\ifdefined\listfigurename
  \renewcommand*\listfigurename{List of Figures}
\else
  \newcommand\listfigurename{List of Figures}
\fi
\ifdefined\listtablename
  \renewcommand*\listtablename{List of Tables}
\else
  \newcommand\listtablename{List of Tables}
\fi
\ifdefined\figurename
  \renewcommand*\figurename{Figure}
\else
  \newcommand\figurename{Figure}
\fi
\ifdefined\tablename
  \renewcommand*\tablename{Table}
\else
  \newcommand\tablename{Table}
\fi
}
\@ifpackageloaded{float}{}{\usepackage{float}}
\floatstyle{ruled}
\@ifundefined{c@chapter}{\newfloat{codelisting}{h}{lop}}{\newfloat{codelisting}{h}{lop}[chapter]}
\floatname{codelisting}{Listing}
\newcommand*\listoflistings{\listof{codelisting}{List of Listings}}
\makeatother
\makeatletter
\@ifpackageloaded{caption}{}{\usepackage{caption}}
\@ifpackageloaded{subcaption}{}{\usepackage{subcaption}}
\makeatother
\makeatletter
\@ifpackageloaded{tcolorbox}{}{\usepackage[skins,breakable]{tcolorbox}}
\makeatother
\makeatletter
\@ifundefined{shadecolor}{\definecolor{shadecolor}{rgb}{.97, .97, .97}}
\makeatother
\makeatletter
\makeatother
\makeatletter
\makeatother
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\urlstyle{same} % disable monospaced font for URLs
\hypersetup{
  pdftitle={My title},
  pdfauthor={Sandy Yu},
  colorlinks=true,
  linkcolor={blue},
  filecolor={Maroon},
  citecolor={Blue},
  urlcolor={Blue},
  pdfcreator={LaTeX via pandoc}}

\title{My title\thanks{Code and data are available at:
https://github.com/Jingying-yu/Shanghai\_population\_change}}
\usepackage{etoolbox}
\makeatletter
\providecommand{\subtitle}[1]{% add subtitle to \maketitle
  \apptocmd{\@title}{\par {\large #1 \par}}{}{}
}
\makeatother
\subtitle{Impact Analysis of Japanese Occupation on Population Shifts
Across Shanghai's Districts During WWII}
\author{Sandy Yu}
\date{November 30, 2024}

\begin{document}
\maketitle
\begin{abstract}
First sentence. Second sentence. Third sentence. Fourth sentence.
\end{abstract}
\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, frame hidden, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

Overview paragraph

Estimand paragraph

Results paragraph

Why it matters paragraph

Telegraphing paragraph: The remainder of this paper is structured as
follows. Section~\ref{sec-data}\ldots.

\hypertarget{sec-data}{%
\section{Data}\label{sec-data}}

\hypertarget{overview}{%
\subsection{Overview}\label{overview}}

We use the statistical programming language R (R Core Team 2023)\ldots.
Our data (Toronto Shelter \& Support Services 2024)\ldots. Following
Alexander (2023), we consider\ldots{}

\hypertarget{data-sources}{%
\subsection{Data Sources}\label{data-sources}}

\begin{itemize}
\tightlist
\item
  talk about where the data in my primary reference book is gathered
\item
  mentions the credibility of source and unstability of recording
  instrument \& methodology
\end{itemize}

\hypertarget{historical-background}{%
\subsection{Historical Background}\label{historical-background}}

Place: Shanghai, China When: 1936-1942 Who: Chinese population in
Shanghai

Define: 1. give 1-2 sentence broad overview of China's state of unrest
2.THREE districts in Shanghai: Chinese District, International
Settlement, French Concession - who controlled each district and the
level of governance each authority have in comparison to Chinese
government 3.Outline area (\%) of each district (do not get into
specifics, put that in Results section)

Important Event Timeline 1. 1937-08-13: Japanese armed forces entered
Shanghai 2. 1937-11-12: Japanese armed forces claims occupation of
Shanghai --\textgreater{} ends Chinese district 3. 1942-01: Japanese
armed forces claims authority over International Settlement (which was
mainly under the governance of U.K and U.S prior to this date) 4.
1945-08-15: Japan surrendered in WWII 5. 1945-10: most Japanese armed
forces withdrawed from Shanghai

\hypertarget{measurement}{%
\subsection{Measurement}\label{measurement}}

\begin{itemize}
\tightlist
\item
  how population is recorded (not accurate count but by householad then
  estimates by average)
\item
  why use population density instead of pure population \#
\item
  how year variables correspond to the timeline (ex. if an event occured
  in Nov of 1937, would I take valeus of 1937 as a variable for prior to
  event occurance or after?)
\end{itemize}

\hypertarget{outcome-variables}{%
\subsection{Outcome variables}\label{outcome-variables}}

\begin{itemize}
\tightlist
\item
  outcome variable is ``population change in International Settlement
  during 1937-1942'' measured in population density
\end{itemize}

\hypertarget{predictor-variables}{%
\subsection{Predictor variables}\label{predictor-variables}}

\begin{itemize}
\tightlist
\item
  most important predictors include time sensitive indicators: Event1 \&
  Event2
\end{itemize}

Event1: indicator variable for 1937 (1 if year \textgreater= 1937 \&
\textless= 1941, 0 otherwise) - mention a bit about the measurement

Event2: indicator variable for 1937 (1 if year \textgreater= 1941, 0
otherwise) - mention a bit about the measurement

\hypertarget{model}{%
\section{Model}\label{model}}

The goal of our modelling strategy is to evaluate the impact of 2
historical events in Shanghai during WWII.

Here we briefly describe the Difference-in-Difference analysis model
used to investigate the impact of the Japanese forces taking over the
Chinese district and International Settlement in November 1937 and
December 1941 on population shift between different Districts in
Shanghai.

Background details and diagnostics are included in
Appendix~\ref{sec-model-details}.

\hypertarget{model-set-up}{%
\subsection{Model set-up}\label{model-set-up}}

\[y_{it}|\mu_{it}, \sigma \sim \mbox{Normal}(\mu_{it}, \sigma)\]

\[\mu_{it} = \alpha + \beta_1 \cdot \mbox{cd_occupied}_{it} + \beta_2 \cdot \mbox{french_surrender}_{it} + \beta_3 \cdot \mbox{is_occupied}_{it} + \beta_4 \cdot \mbox{district_type}_{i, IS} +
\\
\beta_5 \cdot \mbox{district_type}_{i, FC} + \beta_6 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + 
\\
\beta_7 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, FC} + \beta_8 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, IS} + 
\\
\beta_9 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, FC} + 
\\
\beta_{10} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + \beta_{11} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, FC}\]

\[\alpha \sim \mbox{Normal}(0, 2.5)\]

\[\beta_k \sim \mbox{Normal}(0, 2.5) \quad \mbox{for } k = 1, ..., 11\]

\[\sigma \sim \mbox{Exponential}(1)\]

\textbf{Where}:

\begin{itemize}
\tightlist
\item
  \(y_{i,t}\): Observed population in district i at year t.
\item
  \(\mbox{cd_occupied}_{i,t}\): Indicator for whether the
  Chinese-administered district was occupied by Japanese forces in year
  t (1 if \(t \geq 1937\), 0 otherwise).
\item
  \(\mbox{french_surrender}_{i,t}\): Indicator for the French
  Surrendering to Germany in 1940, leading to the French Concession
  rejecting refugees in Shanghai (1 if \(t \geq 1940\), 0 otherwise).
\item
  \(\mbox{is_occupied}_{i,t}\): Indicator for the Japanese occupation of
  the International Settlement in 1942 (1 if \(t \geq 1942\), 0
  otherwise).
\item
  \(\mbox{district_type}_{i, IS}\): Dummy variable for International
  Settlement districts (1 if i is IS, 0 otherwise).
\item
  \(\mbox{district_type}_{i, FC}\): Dummy variable for French Concession
  districts (1 if i is FC, 0 otherwise).
\end{itemize}

\textbf{Interaction Terms}: The interaction terms in the model are
essential because they capture how the impact of historical events
(e.g., the 1937 occupation of Chinese-administered districts, the 1940
refugee rejection in the French Concession, and the 1942 occupation of
the International Settlement) varies across different district types. By
including interactions between event indicators and district types, the
model accounts for district-specific responses to each event,
controlling for the fact that the effect of an event on population
changes may not be uniform across all districts. For instance, the 1937
occupation might lead to population declines in Chinese-administered
districts but population increases in the International Settlement due
to refugee influx. These terms ensure that the model can differentiate
and estimate the unique effects of each event within each district type,
thereby improving precision and interpretability.

\begin{itemize}
\tightlist
\item
  \(\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
  Captures the effect of the 1937 occupation on the International
  Settlement in comparison to the Chinese-administered district (base
  district).
\item
  \(\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
  Captures the effect of the 1937 occupation on the French Concession in
  comparison to the base district.
\item
  \(\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
  Effect of the 1940 refugee rejection on the International Settlement.
\item
  \(\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
  Effect of the 1940 refugee rejection on the French Concession.
\item
  \(\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
  Effect of the 1942 occupation on the International Settlement.
\item
  \(\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
  Effect of the 1942 occupation on the French Concession.
\end{itemize}

We run the model in R (R Core Team 2023) using the \texttt{rstanarm}
package of Goodrich et al. (2022). We use the default priors from
\texttt{rstanarm}.

\hypertarget{model-justification}{%
\subsubsection{Model justification}\label{model-justification}}

We expect a positive relationship between the size of the wings and time
spent aloft. In particular\ldots{}

We can use maths by including latex between dollar signs, for instance
\(\theta\).

\hypertarget{results}{%
\section{Results}\label{results}}

Our results are summarized in Table~\ref{tbl-modelresults}.

\hypertarget{tbl-modelresults}{}
\begin{table}
\caption{\label{tbl-modelresults}Explanatory models of flight time based on wing width and wing length }\tabularnewline

\centering
\begin{tblr}[         %% tabularray outer open
]                     %% tabularray outer close
{                     %% tabularray inner open
colspec={Q[]Q[]},
column{1}={halign=l,},
column{2}={halign=c,},
hline{26}={1,2}{solid, 0.05em, black},
}                     %% tabularray inner close
\toprule
& Population model \\ \midrule %% TinyTableHeader
(Intercept)                                                  & \num{-0.05}      \\
& (\num{15.64})    \\
cd\_occupied                                                & \num{0.15}       \\
& (\num{10.22})    \\
district\_typeFrench Concession                             & \num{-0.11}      \\
& (\num{9.98})     \\
district\_typeInternational Settlement                      & \num{0.07}       \\
& (\num{9.83})     \\
french\_surrender                                           & \num{-0.06}      \\
& (\num{10.22})    \\
is\_occupied                                                & \num{-0.17}      \\
& (\num{9.95})     \\
cd\_occupied × district\_typeFrench Concession             & \num{-0.07}      \\
& (\num{9.95})     \\
cd\_occupied × district\_typeInternational Settlement      & \num{-0.06}      \\
& (\num{9.81})     \\
district\_typeFrench Concession × french\_surrender        & \num{0.01}       \\
& (\num{9.96})     \\
district\_typeInternational Settlement × french\_surrender & \num{-0.02}      \\
& (\num{10.01})    \\
district\_typeFrench Concession × is\_occupied             & \num{0.01}       \\
& (\num{10.20})    \\
district\_typeInternational Settlement × is\_occupied      & \num{0.00}       \\
& (\num{9.85})     \\
Num.Obs.                                                     & \num{21}         \\
R2                                                           & \num{0.000}      \\
Log.Lik.                                                     & \num{-325.376}   \\
RMSE                                                         & \num{1293540.34} \\
\bottomrule
\end{tblr}
\end{table}

\hypertarget{discussion}{%
\section{Discussion}\label{discussion}}

\hypertarget{reason-why-the-french-concession-was-exempted-from-japanese-occupation}{%
\subsection{Reason why the French Concession was Exempted from Japanese
Occupation}\label{reason-why-the-french-concession-was-exempted-from-japanese-occupation}}

\begin{itemize}
\tightlist
\item
  During WWII, on the European battlefield, France surrendered to
  Germany on June 22nd of 1940 (Check this \& reference with a credible
  source). Since Japan was on the same side as Germany during that time,
  Japanese armed forces decided allow the French Concession to retain
  its own governance.
\item
  However, the French Concession is still constantly under the watch of
  the Japanese forces that has occupied the rest of Shanghai since 1942.
  街上不得有侮辱日本的旗帜或者宣言，官方必须积极配合日本统治者进行有利于日本统治的宣传,etc.(can
  reference to video summary here)
\end{itemize}

\hypertarget{refugees-from-outside-of-shanghai-province}{%
\subsection{Refugees from outside of Shanghai
Province}\label{refugees-from-outside-of-shanghai-province}}

\begin{itemize}
\tightlist
\item
  industrialization was not so popular back in the 1930s, many provinces
  are still mostly rural. But warfare messed with the land and the
  yields, causing many farmers to starve and ultimately have to seek
  refugee (find job) in industrialized city (where income is not
  dependent on land yield)
\item
  many people flooded to Shanghai for this reason (can insert
  calculation in data table 20 from reference book here)
\end{itemize}

\hypertarget{job-oppurtunities-in-shanghai}{%
\subsubsection{Job Oppurtunities in
Shanghai}\label{job-oppurtunities-in-shanghai}}

Aside from the instability caused by the Japanese armed forces, there
are a few other reasons for Chinese population to move into the
international settlement \& French Concession. 1. Job opportunities -
Heart of Shanghai city in the 1930-1940s, high pop density lead to boom
of economy = more job opportunities - many factories are located with
the settlements (less so in concession)

\hypertarget{barrier-to-entry-in-job-market}{%
\subsubsection{Barrier to Entry in Job
Market}\label{barrier-to-entry-in-job-market}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  Barrier to Entry for certain job types
\end{enumerate}

\begin{itemize}
\tightlist
\item
  旧时候 --
  通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。
\end{itemize}

\hypertarget{instability-after-japanese-occupation-ends-in-wwii-chinese-civil-war}{%
\subsection{Instability after Japanese Occupation ends in WWII: Chinese
Civil
War}\label{instability-after-japanese-occupation-ends-in-wwii-chinese-civil-war}}

\begin{itemize}
\tightlist
\item
  after the Japanese armed forces withdrawed from Shanghai, what follows
  is not recovery and rest for the local population
\item
  Competition for power within China's 2 political parties caused
  full-scale political warfare, now known as the \emph{Chinese Civil
  War}
\item
  unlike Western political parties, Chinese political parties in the
  1900s are more like parties of a throne. They each have their own
  ideology and an armed forces that follow. Most of all of the provinces
  are effected by this internal warfare, which ended in 1949 as 国民党
  lost and withdrawed to Taiwan.
\end{itemize}

\hypertarget{weaknesses-and-next-steps}{%
\subsection{Weaknesses and next steps}\label{weaknesses-and-next-steps}}

\hypertarget{data-measurement-weaknesses}{%
\subsubsection{Data Measurement
Weaknesses}\label{data-measurement-weaknesses}}

\begin{itemize}
\tightlist
\item
  data was recorded during wartime, many numbers were missing
\item
  base unit for population records is not ppl, it is instead
  ``household''. \# of ppl in a household is estimated based on
  historical data
\item
  many people chose to not report or partially report numbers due to
  convience or economic reasons, data may not be accurate
\end{itemize}

\hypertarget{next-steps}{%
\subsubsection{Next Steps}\label{next-steps}}

\newpage

\appendix

\hypertarget{appendix}{%
\section*{Appendix}\label{appendix}}
\addcontentsline{toc}{section}{Appendix}

\hypertarget{additional-data-details}{%
\section{Additional data details}\label{additional-data-details}}

\hypertarget{sec-model-details}{%
\section{Model details}\label{sec-model-details}}

\hypertarget{posterior-predictive-check}{%
\subsection{Posterior predictive
check}\label{posterior-predictive-check}}

In Figure~\ref{fig-ppcheckandposteriorvsprior-1} we implement a
posterior predictive check. This shows\ldots{}

In Figure~\ref{fig-ppcheckandposteriorvsprior-2} we compare the
posterior with the prior. This shows\ldots{}

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-ppcheckandposteriorvsprior-1.pdf}

}

}

\subcaption{\label{fig-ppcheckandposteriorvsprior-1}Posterior prediction
check}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-ppcheckandposteriorvsprior-2.pdf}

}

}

\subcaption{\label{fig-ppcheckandposteriorvsprior-2}Comparing the
posterior with the prior}
\end{minipage}%

\caption{\label{fig-ppcheckandposteriorvsprior}Examining how the model
fits, and is affected by, the data}

\end{figure}

\hypertarget{diagnostics}{%
\subsection{Diagnostics}\label{diagnostics}}

Figure~\ref{fig-stanareyouokay-1} is a trace plot. It shows\ldots{} This
suggests\ldots{}

Figure~\ref{fig-stanareyouokay-2} is a Rhat plot. It shows\ldots{} This
suggests\ldots{}

\begin{figure}

\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-stanareyouokay-1.pdf}

}

}

\subcaption{\label{fig-stanareyouokay-1}Trace plot}
\end{minipage}%
%
\begin{minipage}[t]{0.50\linewidth}

{\centering

\raisebox{-\height}{

\includegraphics{paper_files/figure-pdf/fig-stanareyouokay-2.pdf}

}

}

\subcaption{\label{fig-stanareyouokay-2}Rhat plot}
\end{minipage}%

\caption{\label{fig-stanareyouokay}Checking the convergence of the MCMC
algorithm}

\end{figure}

\newpage

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-tellingstories}{}}%
Alexander, Rohan. 2023. \emph{Telling Stories with Data}. Chapman;
Hall/CRC. \url{https://tellingstorieswithdata.com/}.

\leavevmode\vadjust pre{\hypertarget{ref-rstanarm}{}}%
Goodrich, Ben, Jonah Gabry, Imad Ali, and Sam Brilleman. 2022.
{``{rstanarm: {Bayesian} applied regression modeling via {Stan}}.''}
\url{https://mc-stan.org/rstanarm/}.

\leavevmode\vadjust pre{\hypertarget{ref-citeR}{}}%
R Core Team. 2023. \emph{{R: A Language and Environment for Statistical
Computing}}. Vienna, Austria: R Foundation for Statistical Computing.
\url{https://www.R-project.org/}.

\leavevmode\vadjust pre{\hypertarget{ref-shelter}{}}%
Toronto Shelter \& Support Services. 2024. \emph{Deaths of Shelter
Residents}.
\url{https://open.toronto.ca/dataset/deaths-of-shelter-residents/}.

\end{CSLReferences}

\end{document}

### 2024-12-01 scripts/03-clean_data.R

@@ -219,8 +219,7 @@ model_format <- combined_data |>
 
 #### Save data ####
 write_parquet(pop_1852_1950, "data/02-analysis_data/pop_analysis_data.parquet")
-write_parquet(cleaned_refugees_data, "data/02-analysis_data/cleaned_refugees_data.parquet")
+write_parquet(year_refugee_summary, "data/02-analysis_data/year_refugee_summary.parquet")
 write_parquet(calibration_percent, "data/02-analysis_data/calibration_percent.parquet")
-write_parquet(combined_data, "data/02-analysis_data/combined_data.parquet")
 write_parquet(model_format, "data/02-analysis_data/model_format.parquet")
-write_csv(model_format, "data/02-analysis_data/model_format.csv")
+

### 2024-12-02 paper/paper.qmd
finished most of the data section, model section, and added to discussion section

@@
 library(arrow)
+library(readr)
 library(knitr)
+library(kableExtra)
 library(modelsummary)
 library(rstanarm)
+library(dplyr)
+library(broom.mixed)
+```
+
+```{r}
+#| include: false
+#| warning: false
+#| message: false
+
+calibration_percent <- read_parquet(file = here::here("data/02-analysis_data/calibration_percent.parquet"))
+year_refugee_summary <- read_parquet(file = here::here("data/02-analysis_data/year_refugee_summary.parquet"))
+combined_data <- read_parquet(file = here::here("data/02-analysis_data/combined_data.parquet"))
+model_format <- read_parquet(file = here::here("data/02-analysis_data/model_format.parquet"))
+did_model <- readRDS(file = here::here("models/did_model.rds"))
 ```
@@
 -   talk about where the data in my primary reference book is gathered
--   mentions the credibility of source and unstability of recording instrument & methodology
+-   mentions the credibility of source and instability of recording instrument & methodology
 
@@
 
-Place: Shanghai, China When: 1936-1942 Who: Chinese population in Shanghai
+Place: Shanghai, China
+
+When: 1936-1942
+
+Who: Chinese population in Shanghai
 
@@
 
-Important Event Timeline 1.
-1937-08-13: Japanese armed forces entered Shanghai 2.
-1937-11-12: Japanese armed forces claims occupation of Shanghai --\> ends Chinese district 3.
-1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date) 4.
-1945-08-15: Japan surrendered in WWII 5.
-1945-10: most Japanese armed forces withdrawed from Shanghai
+Important Event Timeline
 
-## Measurement
+1\. 1937-08-13: Japanese armed forces entered Shanghai
 
--   how population is recorded (not accurate count but by householad then estimates by average)
--   why use population density instead of pure population \#
--   how year variables correspond to the timeline (ex. if an event occured in Nov of 1937, would I take valeus of 1937 as a variable for prior to event occurance or after?)
+2\. 1937-11-12: Japanese armed forces claims occupation of Shanghai --\> ends Chinese district
 
-## Outcome variables
+1940-06-22: France surrendered to Germany --> French Concession stopped taking refugees
 
--   outcome variable is "population change in International Settlement during 1937-1942" measured in population density
+3\. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)
 
-```{r, include = FALSE}
-#| label: fig-planes
-#| fig-cap: Relationship between wing length and width
+4\. 1945-08-15: Japan surrendered in WWII
+
+5\. 1945-10: most Japanese armed forces withdrew from Shanghai
+
+## Measurement & Methodology
+
+-   how population is recorded
+-   Why choose 1936 - 1942 (ex. if an event occurred in Nov of 1937, would I take values of 1937 as a variable for prior to event occurrence or after?)
+
+Survey Difficulties - Population Volatility caused by Warfare: Population is extreme volatile within this time period, population shifts constantly as 战况 proceed - Regional Recording Limitations: Survey response collect difficulty varies between districts.
+- Resistance due to Political Risk
+
+## Variables of Interest
+
+```{r}
 #| echo: false
+#| eval: true
+#| label: tbl-outcome_variable
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
 #| warning: false
@@
 
+knitr::kable(combined_data, col.names = c("Year", "Pop CHN District", "Pop IS", "Pop FC"), align = c("c", "c", "c", "c"))
 ```
 
-## Predictor variables
+### Outcome variable
 
--   most important predictors include time sensitive indicators: Event1 & Event2
+- outcome variable is *population*
 
-Event1: indicator variable for 1937 (1 if year \>= 1937 & \<= 1941, 0 otherwise) - mention a bit about the measurement
+### Predictor variables
+Time variable: year
+Observations used in modelling and other analysis in this paper is ranged between 1936 to 1942.
+No observation is selected before 1936 as the growth pattern varies significantly from the event of our interest (Japanese occupation of Shanghai's different districts), and no value is elected beyond 1942 due to data constraints.
+No annual population records exists on a district bases beyond 1942.
+Foreign districts 解散 in 1949 as new political party came to power and the People's Republic of China was declared.
 
-Event2: indicator variable for 1937 (1 if year \>= 1941, 0 otherwise) - mention a bit about the measurement
+#### Binary Indicators
+District indicators:
+- Variable *district_is* abd *district_fc* are two binary variable used to indicate the district identity of an observation.
+There are 3 possible district identity in Shanghai during 1930s-40s: Chinese-administrated District, International Settlement, and French Concession.
+
+The Chinese-administrated District is governed by local Chinese authority.
+Land type in this area is primary rural, most of the local population are farmers.
+Percentage of foreign (out-of-province) immigrants or refugees is low.
+(@sh) In this analysis paper, Chinese-administrated District takes value of *district_is = 0* and *district_fc = 0* (it is neither International Settlement nor French Concession).
+
+The International Settlement district is a generalized term for section of lands that allowed the occupation of foreign (non-Chinese) residence.
+Foreigners in Shanghai were not allow to reside in areas outside of the bounds of this district.
+Governance power of foreign population within the district -- including the policing, taxing, etc, are transferred to foreign authorities.
+This district takes up most of the central-city in Shanghai during the 1930s-40s, with foreign investment attracting many business opportunities and subsequently job opportunities.
+Due to the complicated political authorities within the district, the part of Shanghai remains initially untouched by the Japanese forces as the entered Shanghai's Chinese-administrated District.
+International Settlement district takes the value of *district_is = 1* and *district_fc = 0* in this paper.
+
+French Concession district is a land district given solely to the French.
+French residency are given the authorization to self-govern within this area.
+Due to political reasons on the Western battlefield, this district remains untouched by the Japanese forces all the way until they withdrew from Shanghai.
+The French Concesion district takes value of *district_is = 0* and *district_fc = 1* for all analysis in the paper.
+
+Historic Event indicators:
+- *cd_occupied*, *french_surrender*, and *is_occupied* are binary variables that mark the whether or not a major historic event that may have impacted Shanghai's population during the observation period (1936-1942) has occured yet.
+1.
+The Japanese armed forces declared occupation of the Chinese-administrated district on 1937-11-12.
+With expectation that Shanghai's population will internally shift out of the Chinese-administrated district, the binary variable *cd_occupied* is used to measure the impact of this event on the population change in Shanghai.
+2.
+As WWII impacted the Eastern globe, on the primary battlefield (Western Battlefield), France surrendered to Germany on 22 June 1940.
+Since Japan sided with Germany in WWII, France's whiteflagging to Germany led to Shanghai's Japanese forces promising not to invade the French Concession on the condition that the district stop taking refugees and support Japanese governance.
+The paper uses the binary variable *french_surrender* to evaluate the impact this event has on the overall population in Shanghai.
+3.
+In January of 1942, the Japanese forces occupied the International Settlement.
+Local authority handed over its governing power to the invading forces.
+This event's impact on Shanghai's population is measuring using the binary variable *is_occupied*.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-d_variables
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+#| message: false
+
+# Select the rows you want
+sliced_table <- model_format |>
+  select(year, population, district_is, district_fc, cd_occupied, french_surrender, is_occupied) |>
+  slice(c(3, 4, 8, 15, 16, 20))
+
+knitr::kable(sliced_table, col.names = c("Year", "Population", "district_is", "district_fc", "cd_occupied", "french_surrender", "is_occupied"), align = c("c", "c", "c", "c", "c", "c", "c"))
+
+```
 
@@
 
-Background details and diagnostics are included in [Appendix -@sec-model-details].
+Background details and diagnostics are included in Appendix \[@sec-model-details\].
 
@@
 
-$$y_{it}|\mu_{it}, \sigma \sim \mbox{Normal}(\mu_{it}, \sigma)$$
+$$y_i|\mu_i, \sigma \sim \text{Normal}(\mu_{i,t}, \sigma)$$
 
-$$\mu_{it} = \alpha + \beta_1 \cdot \mbox{cd_occupied}_{it} + \beta_2 \cdot \mbox{french_surrender}_{it} + \beta_3 \cdot \mbox{is_occupied}_{it} + \beta_4 \cdot \mbox{district_type}_{i, IS} +
-\\
-\beta_5 \cdot \mbox{district_type}_{i, FC} + \beta_6 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + 
-\\
-\beta_7 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, FC} + \beta_8 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, IS} + 
-\\
-\beta_9 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, FC} + 
-\\
-\beta_{10} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + \beta_{11} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, FC}$$
+$$\alpha \sim \text{Normal}(0, 2.5)$$
 
-$$\alpha \sim \mbox{Normal}(0, 2.5)$$
+$$\beta_k \sim \text{Normal}(0, 2.5) \quad \text{for } k = 1, ..., 11$$
 
-$$\beta_k \sim \mbox{Normal}(0, 2.5) \quad \mbox{for } k = 1, ..., 11$$
+$$\sigma \sim \text{Exponential}(1)$$
 
-$$\sigma \sim \mbox{Exponential}(1)$$
+Where:
 
-**Where**:
+-   $y_i$: Observed population in district i at year t.
+-   $\text{cd_occupied}$: Indicator for whether the Chinese-administered district was occupied by Japanese forces in year t (1 if $t \geq 1937$, 0 otherwise).
+-   $\text{french_surrender}$: Indicator for the French Surrendering to Germany in 1940, leading to the French Concession rejecting refugees in Shanghai (1 if $t \geq 1940$, 0 otherwise).
+-   $\text{is_occupied}$: Indicator for the Japanese occupation of the International Settlement in 1942 (1 if $t \geq 1942$, 0 otherwise).
+-   $\text{district_type}$: Dummy variable for International Settlement districts (1 if $i$ is IS, 0 otherwise).
+-   $\text{district_type}$: Dummy variable for French Concession districts (1 if $i$ is FC, 0 otherwise).
 
--   $y_{i,t}$: Observed population in district i at year t.
--   $\mbox{cd_occupied}_{i,t}$: Indicator for whether the Chinese-administered district was occupied by Japanese forces in year t (1 if $t \geq 1937$, 0 otherwise).
--   $\mbox{french_surrender}_{i,t}$: Indicator for the French Surrendering to Germany in 1940, leading to the French Concession rejecting refugees in Shanghai (1 if $t \geq 1940$, 0 otherwise).
--   $\mbox{is_occupied}_{i,t}$: Indicator for the Japanese occupation of the International Settlement in 1942 (1 if $t \geq 1942$, 0 otherwise).
--   $\mbox{district_type}_{i, IS}$: Dummy variable for International Settlement districts (1 if i is IS, 0 otherwise).
--   $\mbox{district_type}_{i, FC}$: Dummy variable for French Concession districts (1 if i is FC, 0 otherwise).
+Interaction Terms:
 
-**Interaction Terms**:
 The interaction terms in the model are essential because they capture how the impact of historical events (e.g., the 1937 occupation of Chinese-administered districts, the 1940 refugee rejection in the French Concession, and the 1942 occupation of the International Settlement) varies across different district types.
@@
 
--   $\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}$: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
--   $\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}$: Captures the effect of the 1937 occupation on the French Concession in comparison to the base district.
--   $\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, IS}$: Effect of the 1940 refugee rejection on the International Settlement.
--   $\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, FC}$: Effect of the 1940 refugee rejection on the French Concession.
--   $\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}$: Effect of the 1942 occupation on the International Settlement.
--   $\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}$: Effect of the 1942 occupation on the French Concession.
+-   $\text{cd_occupied} \cdot \text{district_type}$: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
+-   $\text{cd_occupied} \cdot \text{district_type}$: Captures the effect of the 1937 occupation on the French Concession in comparison to the base district.
+-   $\text{french_surrender} \cdot \text{district_type}$: Effect of the 1940 refugee rejection on the International Settlement.
+-   $\text{french_surrender} \cdot \text{district_type}$: Effect of the 1940 refugee rejection on the French Concession.
+-   $\text{is_occupied} \cdot \text{district_type}$: Effect of the 1942 occupation on the International Settlement.
+-   $\text{is_occupied} \cdot \text{district_type}$: Effect of the 1942 occupation on the French Concession.
 
@@
 
-Our results are summarized in @tbl-modelresults.
+-   Data Trend Visualization
+
+```{r}
+#| label: fig-pop
+#| fig-cap: Population in Shanghai between 1936 - 1942
+#| echo: false
+#| warning: false
+#| message: false
+
+# Create the bar chart with a trend line
+ggplot(model_format, aes(x = year, y = population, fill = district_type, color = district_type)) +
+  geom_bar(stat = "identity", position = "dodge", alpha = 0.7) +  # Bar chart with transparency
+  geom_line(aes(group = district_type), size = 1) +  # Add trend line
+  geom_point(size = 2) +  # Add points on the trend line
+  scale_fill_brewer(palette = "Paired") +  # Use ColorBrewer palette for fill
+  scale_color_brewer(palette = "Paired") +  # Use ColorBrewer palette for trend line
+  labs(
+    title = "Population In Shanghai between 1936-1942",
+    x = "Year",
+    y = "Population",
+    fill = "District Type",
+    color = "District Type"
+  ) +
+  theme_minimal() +
+  theme(
+    legend.position = "bottom",
+    text = element_text(size = 12),
+    plot.title = element_text(hjust = 0.5)
+  )
+```
+
+-   Model results are summarized in @tbl-modelresults in Appendix (@sec-model-details).
 
@@
 
-library(rstanarm)
-
-did_model <-
-  readRDS(file = here::here("models/did_model.rds"))
+# Extract coefficients and statistics as a data frame
+model_summary <- broom.mixed::tidy(did_model)
 ```
 
+#### District Impact on Population
 ```{r}
@@
 #| eval: true
-#| label: tbl-modelresults
+#| label: tbl-district
 #| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
@@
 
-modelsummary::modelsummary(
-  list(
-    "Population model" = did_model
-  ),
-  statistic = "mad",
-  fmt = 2,
-  metrics = c("R2", "RMSE")
-)
+# Filter for the specific coefficient you want (e.g., "cd_occupied")
+d_types <- model_summary |>
+  filter(term %in% c("(Intercept)", "district_is", "district_fc")) |>
+  mutate(
+    estimate = round(estimate, 2),
+    std.error = round(std.error, 2))
+
+knitr::kable(d_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c"))
+```
+
+#### Historical Events
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-events
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+# Filter for the specific coefficient you want (e.g., "cd_occupied")
+event_types <- model_summary |>
+  filter(term %in% c("cd_occupied", "french_surrender", "is_occupied")) |>
+  mutate(
+    estimate = round(estimate, 2),
+    std.error = round(std.error, 2))
+
+knitr::kable(event_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c"))
+```
+
+#### Historic Events' Impact on Each District
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-events_district
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+# Filter for the specific coefficient you want (e.g., "cd_occupied")
+impact_types <- model_summary[7:12, ] |>
+  mutate(estimate = round(estimate, 2),
+    std.error = round(std.error, 2))
+
+print(impact_types)
+knitr::kable(impact_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c", "c", "c", "c"))
 ```
@@
 # Discussion
+
+## Interpretation of the Event Impacts
+
+### Impact of Occupation in Chinese District
+
+### Impact of French Surrendering to Germany on Shanghai
+
+### Impact of Occupation in International Settlement
 
@@
 
+## Model Summary Table
+```{r}
+#| echo: false
+#| eval: true
+#| warning: false
+#| message: false
+
+library(rstanarm)
+
+did_model <-
+  readRDS(file = here::here("models/did_model.rds"))
+```
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+
+modelsummary::modelsummary(
+  list(
+    "Population model" = did_model
+  ),
+  statistic = "mad",
+  fmt = 2,
+  metrics = c("R2", "RMSE")
+)
+```
+
 ## Posterior predictive check

### 2024-12-02 paper/paper.tex
finished most of the data section, model section, and added to discussion section

@@
 
+\usepackage{booktabs}
+\usepackage{longtable}
+\usepackage{array}
+\usepackage{multirow}
+\usepackage{wrapfig}
 \usepackage{float}
+\usepackage{colortbl}
+\usepackage{pdflscape}
+\usepackage{tabu}
+\usepackage{threeparttable}
+\usepackage{threeparttablex}
+\usepackage[normalem]{ulem}
+\usepackage{makecell}
+\usepackage{xcolor}
 \usepackage{tabularray}
@@
 \author{Sandy Yu}
-\date{November 30, 2024}
+\date{December 1, 2024}
 
@@
 \end{abstract}
-\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, breakable, frame hidden, boxrule=0pt, interior hidden, borderline west={3pt}{0pt}{shadecolor}, sharp corners]}{\end{tcolorbox}}\fi
+\ifdefined\Shaded\renewenvironment{Shaded}{\begin{tcolorbox}[enhanced, boxrule=0pt, borderline west={3pt}{0pt}{shadecolor}, frame hidden, breakable, sharp corners, interior hidden]}{\end{tcolorbox}}\fi
 
@@
 \item
-  mentions the credibility of source and unstability of recording
+  mentions the credibility of source and instability of recording
   instrument \& methodology
@@
 
-Place: Shanghai, China When: 1936-1942 Who: Chinese population in
-Shanghai
+Place: Shanghai, China
+
+When: 1936-1942
+
+Who: Chinese population in Shanghai
 
@@
 
-Important Event Timeline 1. 1937-08-13: Japanese armed forces entered
-Shanghai 2. 1937-11-12: Japanese armed forces claims occupation of
-Shanghai --\textgreater{} ends Chinese district 3. 1942-01: Japanese
-armed forces claims authority over International Settlement (which was
-mainly under the governance of U.K and U.S prior to this date) 4.
-1945-08-15: Japan surrendered in WWII 5. 1945-10: most Japanese armed
-forces withdrawed from Shanghai
+Important Event Timeline
 
-\hypertarget{measurement}{%
-\subsection{Measurement}\label{measurement}}
+1. 1937-08-13: Japanese armed forces entered Shanghai
+
+2. 1937-11-12: Japanese armed forces claims occupation of Shanghai
+--\textgreater{} ends Chinese district
+
+3. 1942-01: Japanese armed forces claims authority over International
+Settlement (which was mainly under the governance of U.K and U.S prior
+to this date)
+
+4. 1945-08-15: Japan surrendered in WWII
+
+5. 1945-10: most Japanese armed forces withdrew from Shanghai
+
+\hypertarget{measurement-methodology}{%
+\subsection{Measurement \& Methodology}\label{measurement-methodology}}
 
@@
 \item
-  how population is recorded (not accurate count but by householad then
-  estimates by average)
+  how population is recorded
 \item
-  why use population density instead of pure population \#
-\item
-  how year variables correspond to the timeline (ex. if an event occured
-  in Nov of 1937, would I take valeus of 1937 as a variable for prior to
-  event occurance or after?)
+  Why choose 1936 - 1942 (ex. if an event occurred in Nov of 1937, would
+  I take values of 1937 as a variable for prior to event occurrence or
+  after?)
 \end{itemize}
 
-\hypertarget{outcome-variables}{%
-\subsection{Outcome variables}\label{outcome-variables}}
+Survey Difficulties - Population Volatility caused by Warfare:
+Population is extreme volatile within this time period, population
+shifts constantly as 战况 proceed - Regional Recording Limitations:
+Survey response collect difficulty varies between districts. -
+Resistance due to Political Risk
+
+\hypertarget{variables-of-interest}{%
+\subsection{Variables of Interest}\label{variables-of-interest}}
+
+\hypertarget{tbl-outcome_variable}{}
+\begin{longtable}[]{@{}cccc@{}}
+\caption{\label{tbl-outcome_variable}Explanatory models of flight time
+based on wing width and wing length}\tabularnewline
+\toprule\noalign{}
+Year & Pop CHN District & Pop IS & Pop FC \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Year & Pop CHN District & Pop IS & Pop FC \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+1936 & 2155717 & 1180969 & 477629 \\
+1937 & 2155717 & 1218630 & 477629 \\
+1938 & 2074693 & 1272552 & 504731 \\
+1939 & 2098331 & 1257703 & 495942 \\
+1940 & 1479726 & 1233394 & 477629 \\
+1941 & 957339 & 446692 & 835523 \\
+1942 & 1049403 & 1585673 & 854380 \\
+\end{longtable}
+
+\hypertarget{outcome-variable}{%
+\subsubsection{Outcome variable}\label{outcome-variable}}
 
@@
 \item
-  outcome variable is ``population change in International Settlement
-  during 1937-1942'' measured in population density
+  outcome variable is \emph{population} with subscript of time (t) and
+  district (i), where time range is between 1936-1942, and district is
+  either: Chinese-administrated District, International Settlement, and
+  French Concession. ``population change in International Settlement
+  during 1937-1942'' measured in \# of persons
 \end{itemize}
@@
 \hypertarget{predictor-variables}{%
-\subsection{Predictor variables}\label{predictor-variables}}
+\subsubsection{Predictor variables}\label{predictor-variables}}
 
@@
 \item
-  most important predictors include time sensitive indicators: Event1 \&
-  Event2
+  Event indicators (dummy variables)
 \end{itemize}
 
-Event1: indicator variable for 1937 (1 if year \textgreater= 1937 \&
-\textless= 1941, 0 otherwise) - mention a bit about the measurement
+\begin{table}
 
-Event2: indicator variable for 1937 (1 if year \textgreater= 1941, 0
-otherwise) - mention a bit about the measurement
+\end{table}
 
@@
 
-Background details and diagnostics are included in
-Appendix~\ref{sec-model-details}.
+Background details and diagnostics are included in Appendix
+{[}Section~\ref{sec-model-details}{]}.
 
@@
 
-\[y_{it}|\mu_{it}, \sigma \sim \mbox{Normal}(\mu_{it}, \sigma)\]
+\[y_i|\mu_i, \sigma \sim \text{Normal}(\mu_{i,t}, \sigma)\]
 
-\[\mu_{it} = \alpha + \beta_1 \cdot \mbox{cd_occupied}_{it} + \beta_2 \cdot \mbox{french_surrender}_{it} + \beta_3 \cdot \mbox{is_occupied}_{it} + \beta_4 \cdot \mbox{district_type}_{i, IS} +
-\\
-\beta_5 \cdot \mbox{district_type}_{i, FC} + \beta_6 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + 
-\\
-\beta_7 \cdot \mbox{cd_occupied}_{it} \cdot \mbox{district_type}_{i, FC} + \beta_8 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, IS} + 
-\\
-\beta_9 \cdot \mbox{french_surrender}_{it} \cdot \mbox{district_type}_{i, FC} + 
-\\
-\beta_{10} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, IS} + \beta_{11} \cdot \mbox{is_occupied}_{it} \cdot \mbox{district_type}_{i, FC}\]
+\[\alpha \sim \text{Normal}(0, 2.5)\]
 
-\[\alpha \sim \mbox{Normal}(0, 2.5)\]
+\[\beta_k \sim \text{Normal}(0, 2.5) \quad \text{for } k = 1, ..., 11\]
 
-\[\beta_k \sim \mbox{Normal}(0, 2.5) \quad \mbox{for } k = 1, ..., 11\]
+\[\sigma \sim \text{Exponential}(1)\]
 
-\[\sigma \sim \mbox{Exponential}(1)\]
-
-\textbf{Where}:
+Where:
 
@@
 \item
-  \(y_{i,t}\): Observed population in district i at year t.
+  \(y_i\): Observed population in district i at year t.
 \item
-  \(\mbox{cd_occupied}_{i,t}\): Indicator for whether the
-  Chinese-administered district was occupied by Japanese forces in year
-  t (1 if \(t \geq 1937\), 0 otherwise).
+  \(\text{cd_occupied}\): Indicator for whether the Chinese-administered
+  district was occupied by Japanese forces in year t (1 if
+  \(t \geq 1937\), 0 otherwise).
 \item
-  \(\mbox{french_surrender}_{i,t}\): Indicator for the French
-  Surrendering to Germany in 1940, leading to the French Concession
-  rejecting refugees in Shanghai (1 if \(t \geq 1940\), 0 otherwise).
+  \(\text{french_surrender}\): Indicator for the French Surrendering to
+  Germany in 1940, leading to the French Concession rejecting refugees
+  in Shanghai (1 if \(t \geq 1940\), 0 otherwise).
 \item
-  \(\mbox{is_occupied}_{i,t}\): Indicator for the Japanese occupation of
-  the International Settlement in 1942 (1 if \(t \geq 1942\), 0
-  otherwise).
+  \(\text{is_occupied}\): Indicator for the Japanese occupation of the
+  International Settlement in 1942 (1 if \(t \geq 1942\), 0 otherwise).
 \item
-  \(\mbox{district_type}_{i, IS}\): Dummy variable for International
-  Settlement districts (1 if i is IS, 0 otherwise).
+  \(\text{district_type}\): Dummy variable for International Settlement
+  districts (1 if \(i\) is IS, 0 otherwise).
 \item
-  \(\mbox{district_type}_{i, FC}\): Dummy variable for French Concession
-  districts (1 if i is FC, 0 otherwise).
+  \(\text{district_type}\): Dummy variable for French Concession
+  districts (1 if \(i\) is FC, 0 otherwise).
 \end{itemize}
 
-\textbf{Interaction Terms}: The interaction terms in the model are
-essential because they capture how the impact of historical events
-(e.g., the 1937 occupation of Chinese-administered districts, the 1940
-refugee rejection in the French Concession, and the 1942 occupation of
-the International Settlement) varies across different district types. By
-including interactions between event indicators and district types, the
-model accounts for district-specific responses to each event,
-controlling for the fact that the effect of an event on population
-changes may not be uniform across all districts. For instance, the 1937
-occupation might lead to population declines in Chinese-administered
-districts but population increases in the International Settlement due
-to refugee influx. These terms ensure that the model can differentiate
-and estimate the unique effects of each event within each district type,
-thereby improving precision and interpretability.
+Interaction Terms:
+
+The interaction terms in the model are essential because they capture
+how the impact of historical events (e.g., the 1937 occupation of
+Chinese-administered districts, the 1940 refugee rejection in the French
+Concession, and the 1942 occupation of the International Settlement)
+varies across different district types. By including interactions
+between event indicators and district types, the model accounts for
+district-specific responses to each event, controlling for the fact that
+the effect of an event on population changes may not be uniform across
+all districts. For instance, the 1937 occupation might lead to
+population declines in Chinese-administered districts but population
+increases in the International Settlement due to refugee influx. These
+terms ensure that the model can differentiate and estimate the unique
+effects of each event within each district type, thereby improving
+precision and interpretability.
 
@@
 \item
-  \(\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
-  Captures the effect of the 1937 occupation on the International
-  Settlement in comparison to the Chinese-administered district (base
-  district).
+  \(\text{cd_occupied} \cdot \text{district_type}\): Captures the effect
+  of the 1937 occupation on the International Settlement in comparison
+  to the Chinese-administered district (base district).
 \item
-  \(\mbox{cd_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
-  Captures the effect of the 1937 occupation on the French Concession in
-  comparison to the base district.
+  \(\text{cd_occupied} \cdot \text{district_type}\): Captures the effect
+  of the 1937 occupation on the French Concession in comparison to the
+  base district.
 \item
-  \(\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
-  Effect of the 1940 refugee rejection on the International Settlement.
+  \(\text{french_surrender} \cdot \text{district_type}\): Effect of the
+  1940 refugee rejection on the International Settlement.
 \item
-  \(\mbox{french_surrender}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
-  Effect of the 1940 refugee rejection on the French Concession.
+  \(\text{french_surrender} \cdot \text{district_type}\): Effect of the
+  1940 refugee rejection on the French Concession.
 \item
-  \(\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, IS}\):
-  Effect of the 1942 occupation on the International Settlement.
+  \(\text{is_occupied} \cdot \text{district_type}\): Effect of the 1942
+  occupation on the International Settlement.
 \item
-  \(\mbox{is_occupied}_{i,t} \cdot \mbox{district_type}_{i, FC}\):
-  Effect of the 1942 occupation on the French Concession.
+  \(\text{is_occupied} \cdot \text{district_type}\): Effect of the 1942
+  occupation on the French Concession.
 \end{itemize}
@@
 
-Our results are summarized in Table~\ref{tbl-modelresults}.
+\begin{itemize}
+\tightlist
+\item
+  Data Trend Visualization
+\end{itemize}
 
-\hypertarget{tbl-modelresults}{}
-\begin{table}
-\caption{\label{tbl-modelresults}Explanatory models of flight time based on wing width and wing length }\tabularnewline
+\begin{figure}
 
-\centering
-\begin{tblr}[         %% tabularray outer open
-]                     %% tabularray outer close
-{                     %% tabularray inner open
-colspec={Q[]Q[]},
-column{1}={halign=l,},
-column{2}={halign=c,},
-hline{26}={1,2}{solid, 0.05em, black},
-}                     %% tabularray inner close
-\toprule
-& Population model \\ \midrule %% TinyTableHeader
-(Intercept)                                                  & \num{-0.05}      \\
-& (\num{15.64})    \\
-cd\_occupied                                                & \num{0.15}       \\
-& (\num{10.22})    \\
-district\_typeFrench Concession                             & \num{-0.11}      \\
-& (\num{9.98})     \\
-district\_typeInternational Settlement                      & \num{0.07}       \\
-& (\num{9.83})     \\
-french\_surrender                                           & \num{-0.06}      \\
-& (\num{10.22})    \\
-is\_occupied                                                & \num{-0.17}      \\
-& (\num{9.95})     \\
-cd\_occupied × district\_typeFrench Concession             & \num{-0.07}      \\
-& (\num{9.95})     \\
-cd\_occupied × district\_typeInternational Settlement      & \num{-0.06}      \\
-& (\num{9.81})     \\
-district\_typeFrench Concession × french\_surrender        & \num{0.01}       \\
-& (\num{9.96})     \\
-district\_typeInternational Settlement × french\_surrender & \num{-0.02}      \\
-& (\num{10.01})    \\
-district\_typeFrench Concession × is\_occupied             & \num{0.01}       \\
-& (\num{10.20})    \\
-district\_typeInternational Settlement × is\_occupied      & \num{0.00}       \\
-& (\num{9.85})     \\
-Num.Obs.                                                     & \num{21}         \\
-R2                                                           & \num{0.000}      \\
-Log.Lik.                                                     & \num{-325.376}   \\
-RMSE                                                         & \num{1293540.34} \\
-\bottomrule
-\end{tblr}
-\end{table}
+{\centering \includegraphics{paper_files/figure-pdf/fig-pop-1.pdf}
+
+}
+
+\caption{\label{fig-pop}Population in Shanghai between 1936 - 1942}
+
+\end{figure}
+
+\begin{itemize}
+\tightlist
+\item
+  Model results are summarized in Table~\ref{tbl-modelresults} in
+  Appendix (Section~\ref{sec-model-details}).
+\end{itemize}
+
+\hypertarget{district-impact-on-population}{%
+\paragraph{District Impact on
+Population}\label{district-impact-on-population}}
+
+\hypertarget{tbl-district}{}
+\begin{longtable}[]{@{}ccc@{}}
+\caption{\label{tbl-district}Explanatory models of flight time based on
+wing width and wing length}\tabularnewline
+\toprule\noalign{}
+Parameters & Estimated Effect & Standard Error \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Parameters & Estimated Effect & Standard Error \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+(Intercept) & 117928165.6 & 189545438.8 \\
+district\_is & -943281.6 & 381299.4 \\
+district\_fc & -1642126.9 & 350808.4 \\
+\end{longtable}
+
+\hypertarget{historical-events}{%
+\paragraph{Historical Events}\label{historical-events}}
+
+\hypertarget{tbl-events}{}
+\begin{longtable}[]{@{}ccc@{}}
+\caption{\label{tbl-events}Explanatory models of flight time based on
+wing width and wing length}\tabularnewline
+\toprule\noalign{}
+Parameters & Estimated Effect & Standard Error \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Parameters & Estimated Effect & Standard Error \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+cd\_occupied & 89350.01 & 350665.6 \\
+french\_surrender & -735223.28 & 340852.1 \\
+is\_occupied & -88982.32 & 361506.9 \\
+\end{longtable}
+
+\hypertarget{historic-events-impact-on-each-district}{%
+\paragraph{Historic Events' Impact on Each
+District}\label{historic-events-impact-on-each-district}}
+
+\begin{verbatim}
+# A tibble: 6 x 3
+  term                         estimate std.error
+  <chr>                           <dbl>     <dbl>
+1 is_occupied                   -88982.   361507.
+2 district_is:cd_occupied        89431.   414727.
+3 district_fc:cd_occupied        38397.   410271.
+4 district_is:french_surrender  470618.   352216.
+5 district_fc:french_surrender 1044471.   352470.
+6 district_is:is_occupied       934059.   476934.
+\end{verbatim}
+
+\hypertarget{tbl-events_district}{}
+\begin{longtable}[]{@{}ccc@{}}
+\caption{\label{tbl-events_district}Explanatory models of flight time
+based on wing width and wing length}\tabularnewline
+\toprule\noalign{}
+Parameters & Estimated Effect & Standard Error \\
+\midrule\noalign{}
+\endfirsthead
+\toprule\noalign{}
+Parameters & Estimated Effect & Standard Error \\
+\midrule\noalign{}
+\endhead
+\bottomrule\noalign{}
+\endlastfoot
+is\_occupied & -88982.32 & 361506.9 \\
+district\_is:cd\_occupied & 89430.69 & 414726.8 \\
+district\_fc:cd\_occupied & 38396.87 & 410271.2 \\
+district\_is:french\_surrender & 470617.65 & 352215.9 \\
+district\_fc:french\_surrender & 1044470.54 & 352469.9 \\
+district\_is:is\_occupied & 934059.10 & 476934.2 \\
+\end{longtable}
 
@@
 \section{Discussion}\label{discussion}}
+
+\hypertarget{interpretation-of-the-event-impacts}{%
+\subsection{Interpretation of the Event
+Impacts}\label{interpretation-of-the-event-impacts}}
 
@@
 
+\hypertarget{model-summary-table}{%
+\subsection{Model Summary Table}\label{model-summary-table}}
+
+\hypertarget{tbl-modelresults}{}
+\begin{table}
+\caption{\label{tbl-modelresults}Explanatory models of flight time based on wing width and wing length }\tabularnewline
+
+\centering
+\begin{tblr}[         %% tabularray outer open
+]                     %% tabularray outer close
+{                     %% tabularray inner open
+colspec={Q[]Q[]},
+column{1}={halign=l,},
+column{2}={halign=c,},
+hline{28}={1,2}{solid, 0.05em, black},
+}                     %% tabularray inner close
+\toprule
+& Population model \\ \midrule %% TinyTableHeader
+(Intercept)                        & \num{117928165.58}   \\
+& (\num{189545438.85}) \\
+year                               & \num{-59841.02}      \\
+& (\num{98298.59})     \\
+district\_is                      & \num{-943281.63}     \\
+& (\num{381299.41})    \\
+district\_fc                      & \num{-1642126.91}    \\
+& (\num{350808.44})    \\
+cd\_occupied                      & \num{89350.01}       \\
+& (\num{350665.57})    \\
+french\_surrender                 & \num{-735223.28}     \\
+& (\num{340852.10})    \\
+is\_occupied                      & \num{-88982.32}      \\
+& (\num{361506.88})    \\
+district\_is × cd\_occupied      & \num{89430.69}       \\
+& (\num{414726.84})    \\
+district\_fc × cd\_occupied      & \num{38396.87}       \\
+& (\num{410271.18})    \\
+district\_is × french\_surrender & \num{470617.65}      \\
+& (\num{352215.89})    \\
+district\_fc × french\_surrender & \num{1044470.54}     \\
+& (\num{352469.86})    \\
+district\_is × is\_occupied      & \num{934059.10}      \\
+& (\num{476934.16})    \\
+district\_fc × is\_occupied      & \num{377436.02}      \\
+& (\num{466616.20})    \\
+Num.Obs.                           & \num{21}             \\
+R2                                 & \num{0.837}          \\
+Log.Lik.                           & \num{-289.106}       \\
+RMSE                               & \num{162825.22}      \\
+\bottomrule
+\end{tblr}
+\end{table}
+
 \hypertarget{posterior-predictive-check}{%

### 2024-12-02 scripts/04-test_analysis_data.R

@@ -9,13 +9,15 @@
 
 
 #### Workspace setup ####
+library(tidyverse)
+library(testthat)
+library(arrow)
+
+
 model_format <- read_parquet("data/02-analysis_data/model_format.parquet")
 year_refugee_summary <- read_parquet("data/02-analysis_data/year_refugee_summary.parquet")
 calibration_percent <- read_parquet("data/02-analysis_data/calibration_percent.parquet")
 
-library(tidyverse)
-library(testthat)
-library(arrow)
 
 #### Test data ####
 

### 2024-12-02 scripts/06-model_data.R

@@ -19,15 +19,24 @@ model_format <- read_parquet("data/02-analysis_data/model_format.parquet")
 ### Model data ####
 
 did_model <- stan_glm(
-  population ~ cd_occupied * district_type + 
-    french_surrender * district_type + 
-    is_occupied * district_type,
+  population ~ year + district_is + district_fc + cd_occupied * district_is + 
+    cd_occupied * district_fc +
+    french_surrender * district_is + 
+    french_surrender * district_fc +
+    is_occupied * district_is + 
+    is_occupied * district_fc,
   data = model_format,
   family = gaussian(),  # Continuous dependent variable
-  prior = normal(0, 10),  # Weakly informative prior
-  prior_intercept = normal(0, 10),
-  chains = 4, iter = 2000, seed = 123
+  prior = normal(location = 0, scale = 2.5, autoscale = TRUE),
+  prior_intercept = normal(0, 2.5, autoscale = TRUE),
+  prior_aux = exponential(rate = 1, autoscale = TRUE),
+  seed = 853
 )
+
+
+
+
+
 
 
 #### Save model ####

### 2024-12-02 paper/paper.qmd
deleted unused files and finded abstract

@@
 date-format: long
-abstract: "First sentence. Second sentence. Third sentence. Fourth sentence."
+abstract: "This paper evaluates the impact of three historic events on the population dynamics of Shanghai during WWII: the Japanese occupation of the Chinese-administered area, France’s surrender in WWII, and the Japanese occupation of the International Settlement.
+Data from the Virtual Shanghai research platform and historic publications are analyzed using a difference-in-difference model to estimate the effects of these events.
+The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts.
+In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession.
+Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself.
+These findings underscore the complex demographic shifts resulting from geopolitical events and reveal how wartime occupation reshaped urban populations in uneven ways, reflecting resilience and displacement patterns."
 format: pdf
@@
 
-Telegraphing paragraph: The remainder of this paper is structured as follows. @sec-data....
+Analyses and findings in this paper are structured into several sections: @sec-data -- Data, @sec-model – Model, @sec-results -- Results, and @sec-discussion -- Discussion.
+The Data section examines all variables and attributes kept for analysis, followed by an explanation of their measurement and purpose.
+The Model section defines the generalized linear model used for further analysis, explain its components, and presents model justifications.
+The Result section focuses on visualizing and presenting the model results through data presented in Data section.
+The Discussion section further evaluate the interpretations behind the model results presented in the previous section, and touches on any expanded topics as well as weaknesses and next steps.
 
@@
 
-We use the statistical programming language R [@citeR].... Our data [@shelter].... Following @tellingstories, we consider...
+Data is cleaned and analyzed using the open-source statistical programming language R [@citeR] and supporting packages including tidyverse [@tidyverse], arrow [@arrow], readr [@readr], knitr [@knitr], kableExtra [@kableExtra], modelsummary [@modelsummary], rstanarm [@rstanarm], dplyr [@dplyr], and broom.mixed [@broom.mixed].
+These tools facilitate data manipulation, visualization, modeling, and reporting.
+Detailed descriptions of each dataset are provided in the subsections below.
 
@@
 
-1940-06-22: France surrendered to Germany --> French Concession stopped taking refugees
+1940-06-22: France surrendered to Germany --\> French Concession stopped taking refugees
 
@@
 ### Predictor variables
-Time variable: year
-Observations used in modelling and other analysis in this paper is ranged between 1936 to 1942.
+
+Time variable: year Observations used in modelling and other analysis in this paper is ranged between 1936 to 1942.
 No observation is selected before 1936 as the growth pattern varies significantly from the event of our interest (Japanese occupation of Shanghai's different districts), and no value is elected beyond 1942 due to data constraints.
@@
 #### Binary Indicators
-District indicators:
-- Variable *district_is* abd *district_fc* are two binary variable used to indicate the district identity of an observation.
+
+District indicators: - Variable *district_is* abd *district_fc* are two binary variable used to indicate the district identity of an observation.
 There are 3 possible district identity in Shanghai during 1930s-40s: Chinese-administrated District, International Settlement, and French Concession.
@@
 
-Historic Event indicators:
-- *cd_occupied*, *french_surrender*, and *is_occupied* are binary variables that mark the whether or not a major historic event that may have impacted Shanghai's population during the observation period (1936-1942) has occured yet.
+Historic Event indicators: - *cd_occupied*, *french_surrender*, and *is_occupied* are binary variables that mark the whether or not a major historic event that may have impacted Shanghai's population during the observation period (1936-1942) has occured yet.
 1.
@@
 
-Background details and diagnostics are included in Appendix \[@sec-model-details\].
+Background details and diagnostics are included in Appendix [@sec-model-details].
 
@@
 
+$$\mu_i = \alpha + \beta_k$$
 $$\alpha \sim \text{Normal}(0, 2.5)$$
 
-$$\beta_k \sim \text{Normal}(0, 2.5) \quad \text{for } k = 1, ..., 11$$
+$$\beta_k \sim \text{Normal}(0, 2.5) \quad \text{for } k = 1, ..., 12$$
 
@@
 -   $y_i$: Observed population in district i at year t.
--   $\text{cd_occupied}$: Indicator for whether the Chinese-administered district was occupied by Japanese forces in year t (1 if $t \geq 1937$, 0 otherwise).
--   $\text{french_surrender}$: Indicator for the French Surrendering to Germany in 1940, leading to the French Concession rejecting refugees in Shanghai (1 if $t \geq 1940$, 0 otherwise).
--   $\text{is_occupied}$: Indicator for the Japanese occupation of the International Settlement in 1942 (1 if $t \geq 1942$, 0 otherwise).
--   $\text{district_type}$: Dummy variable for International Settlement districts (1 if $i$ is IS, 0 otherwise).
--   $\text{district_type}$: Dummy variable for French Concession districts (1 if $i$ is FC, 0 otherwise).
+-   $\alpha$: The intercept for when all variables take value of 0.
+-   $\beta_1$: coefficient for temporal observation *year*. Controls for the effect of time (on an annual basis) on Shanghai's population.
+-   $\beta_2$: coefficient for the dummy variable *district_is*.
+Take on value of 1 if the district of the observation is International Settlement districts (1 if *district type* is IS, 0 otherwise).
+The coefficient measures the effect of district identity on population of Shanghai within a given year.
+-   $\beta_3$: *district_fc*: Dummy variable for French Concession districts (1 if $i$ is FC, 0 otherwise).
+The coefficient measures the effect of district identity on population of Shanghai within a given year.
+-   $\beta_4$: the coefficient for *cd_occupied* indicator.
+This indicator takes a value of 1 after the Chinese-administered district was occupied by Japanese forces in year 1937 (1 if $t \geq 1937$, 0 otherwise).
+The coefficient measures the effect of this indicator on population of Shanghai within a given year.
+-   $\beta_5$: coefficient for indicator *french_surrender* which takes on a value of *1* after the French Surrendering to Germany in 1940, leading to the French Concession rejecting refugees in Shanghai (1 if $t \geq 1940$, 0 otherwise).
+The coefficient measures the effect of this indicator on population of Shanghai within a given year.
+-   $\beta_6$: the coefficient for the indicator *is_occupied*.
+This indicator marks the Japanese occupation of the International Settlement in 1942 (1 if $t \geq 1942$, 0 otherwise).
+The coefficient measures the effect of this indicator on population of Shanghai within a given year.
+-   $\beta_i\ where\ i = 7, ..., 12$: coefficients for interaction terms below. Each term ajusts the impact of a historical events on a district-specific basis.
 
@@
 
--   $\text{cd_occupied} \cdot \text{district_type}$: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
--   $\text{cd_occupied} \cdot \text{district_type}$: Captures the effect of the 1937 occupation on the French Concession in comparison to the base district.
--   $\text{french_surrender} \cdot \text{district_type}$: Effect of the 1940 refugee rejection on the International Settlement.
--   $\text{french_surrender} \cdot \text{district_type}$: Effect of the 1940 refugee rejection on the French Concession.
--   $\text{is_occupied} \cdot \text{district_type}$: Effect of the 1942 occupation on the International Settlement.
--   $\text{is_occupied} \cdot \text{district_type}$: Effect of the 1942 occupation on the French Concession.
+-   *district_is × cd_occupied*: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
+-   *district_fc × cd_occupied*: Captures the effect of the 1937 occupation on the French Concession in comparison to the base district.
+-   *district_is × french_surrender*: Effect of the 1940 refugee rejection on the International Settlement.
+-   *district_fc × french_surrender*: Effect of the 1940 refugee rejection on the French Concession.
+-   *district_is × is_occupied*: Effect of the 1942 occupation on the International Settlement.
+-   *district_fc × is_occupied*: Effect of the 1942 occupation on the French Concession.
 
@@
 #### District Impact on Population
+
 ```{r}
@@
 #### Historical Events
+
 ```{r}
@@
 #### Historic Events' Impact on Each District
+
 ```{r}
@@
 ## Model Summary Table
+
 ```{r}
@@
 
+# Appendix B: Idealized Survey Methodology
+
+This appendix presents an idealized design for a population sampling survey, assuming that a data-recorder has unlimited time and authority to collect data within the historical timeframe of 1936–1942.
+The proposed methodology outlines a systematic approach to gathering detailed population data from Shanghai’s districts during pivotal wartime events, with considerations for the practical constraints and technology available during that period.
+While acknowledging the inherent challenges of conducting such a survey, this design aims to provide a comprehensive framework for understanding population dynamics within the Chinese-administered areas, International Settlement, and French Concession.
+
+## Objective of the Survey
+
+The purpose of this survey is to evaluate the relationship between key historical events and population shifts within Shanghai’s districts between 1936 and 1942.
+Specifically, the study aims to document the population changes in three major districts—Chinese-administered areas, International Settlement, and French Concession—during pivotal events such as the 1937 Japanese occupation of Chinese districts, the 1940 rejection of refugees in the French Concession, and the 1942 occupation of the International Settlement.
+
+## Target Population
+
+The survey targets residents and local representatives from the three major districts of Shanghai.
+These include long-term residents who were present before and during the historical events under study, as well as recent migrants and refugees arriving in these districts as a result of wartime displacement.
+The goal is to achieve representative coverage across the three districts to capture the diversity in population trends and movement patterns.
+
+## Sampling Design
+
+The sampling design employs stratified random sampling to ensure representation across the three major districts.
+Each district is treated as a separate stratum: Chinese-administered areas, International Settlement, and French Concession.
+A fixed number of households per district are selected based on district size, population density, and anticipated population shifts.
+Special attention is given to refugee populations within the International Settlement and French Concession to capture the impact of displacement.
+Enumerators use household lists and local community organizations, such as neighborhood associations and refugee aid committees, to randomly select respondents within strata.
+
+## Recruitment Strategy
+
+The recruitment strategy involves direct engagement with local leaders, community groups, and refugee aid organizations.
+Enumerators collaborate with influential figures in each district to gain trust and permission to conduct the survey.
+Recruitment booths are set up in public spaces such as markets and parks to engage with potential respondents.
+Additionally, refugee aid centers are utilized to access displaced populations.
+Recruitment materials are printed in both Chinese and English to accommodate the linguistic diversity of Shanghai’s residents.
+
+## Survey Instrument
+
+The survey instrument consists of a structured questionnaire covering demographic information, migration history, wartime impact, and population and housing details.
+The demographic section collects age, gender, occupation, family size, and household composition.
+Migration history includes the origin, year of migration to the current district, and reasons for relocation.
+Wartime impact focuses on displacement, property loss, and wartime experiences.
+Lastly, the population and housing section gathers data on the number of residents, housing type, and living conditions.
+Open-ended questions are also included to capture respondents’ personal narratives about wartime displacement and resettlement.
+
+## Data Collection Procedures
+
+Data collection occurs between 1936 and 1942, with enumerators visiting households, public spaces, and refugee shelters.
+Enumerators are trained to conduct interviews in Chinese, Shanghainese, or English based on respondent preferences.
+Responses are recorded on pre-printed forms, which are later transcribed and stored securely.
+To ensure accuracy, enumerators cross-check entries at the end of each survey day.
+Each enumerator is assigned a specific district to maintain consistency in data collection practices.
+
+## Limitations and Challenges
+
+Some areas, particularly those under military occupation, may not be accessible for data collection, leading to incomplete coverage.
+Additionally, respondents may underreport family size or migration history due to privacy concerns or fear of government reprisal.
+Refugee populations are often transient and may not remain in one location long enough for follow-up interviews.
+Despite these limitations, the survey employs robust sampling and recruitment strategies to mitigate potential biases.
+
+## Ethical Considerations
+
+Informed consent is obtained by informing respondents about the purpose of the survey and how their data will be used before they agree to participate.
+Personal identifying information is anonymized to ensure respondent privacy and security.
+Participation is entirely voluntary, and respondents can opt out at any time without consequences.
+The survey complies with ethical standards to respect the rights and dignity of all participants.
+
 \newpage

### 2024-12-02 paper/paper.qmd
added title and changed formatting

@@
 ---
-title: "My title"
+title: "WWII Events Reduce Population in One Shanghai District While Increasing It in Others"
 subtitle: "Impact Analysis of Japanese Occupation on Population Shifts Across Shanghai’s Districts During WWII"
@@
 
-Where:
+**Where**:
 
@@
 
-Interaction Terms:
+**Interaction Terms**:
 
@@
 
-# Appendix B: Idealized Survey Methodology
+\newpage
+
+# Idealized Survey Methodology
 

### 2024-12-03 scripts/03-clean_data.R
updated preambles for scripts and deleted unused files

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Cleans the raw plane data recorded by two observers..... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 6 April 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Cleans the raw Shanghai population data
+# Author: Sandy Yu
+# Date: 16 November 2024
+# Contact: jingying.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: obtained raw data and created simulated plan of data
+
 
 #### Workspace setup ####
 library(tidyverse)

### 2024-12-03 scripts/04-test_analysis_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Tests... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 26 September 2024 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: Tests the cleaned data to ensure data cleaning procedure is done correctly
+# Author: Sandy Yu
+# Date: 16 November 2024
+# Contact: jingying.yu@mail.utoronto.ca]
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: cleaned raw data and saved to correct folder
+
 
 
 #### Workspace setup ####

### 2024-12-03 scripts/06-model_data.R

@@ -1,11 +1,11 @@
 #### Preamble ####
-# Purpose: Models... [...UPDATE THIS...]
-# Author: Rohan Alexander [...UPDATE THIS...]
-# Date: 11 February 2023 [...UPDATE THIS...]
-# Contact: rohan.alexander@utoronto.ca [...UPDATE THIS...]
+# Purpose: use analysis data to model for relationship between variables
+# Author: Sandy Yu
+# Date: 16 November 2024
+# Contact: jingying.yu@mail.utoronto.ca
 # License: MIT
-# Pre-requisites: [...UPDATE THIS...]
-# Any other information needed? [...UPDATE THIS...]
+# Pre-requisites: have sufficient modelling knowledge to understand which model to use, and has obtained cleaned data
+
 
 
 #### Workspace setup ####

### 2024-12-03 paper/paper.qmd
updated result section

@@
 # Results
+This section presents the population trends in Shanghai’s districts between 1936 and 1942, the estimated effects of district type and key historical events on population, and the district-specific impacts of these events as captured by interaction terms.
+The analysis highlights distinct population shifts driven by both district characteristics and the varying effects of war-related events.
 
--   Data Trend Visualization
+## Population Trend
 
@@
 ```
+The population trends from 1936 to 1942 reveal distinct shifts across the three districts in Shanghai: the Chinese-administered area, the French Concession, and the International Settlement.
+In the Chinese-administered area, the population remained stable until 1937, after which a decline began in 1940, continuing through 1942.
+The International Settlement experienced consistent population growth throughout the period, with the largest increases occurring after 1938.
+The French Concession maintained population stability until 1940, followed by a slight increase in 1941, which plateaued in 1942.
 
--   Model results are summarized in @tbl-modelresults in Appendix (@sec-model-details).
+## Model results
+
+Model results are summarized in @tbl-modelresults in Appendix (@sec-model-details).
 
@@
 
-#### District Impact on Population
+### District Impact on Population
 
@@
 d_types <- model_summary |>
-  filter(term %in% c("(Intercept)", "district_is", "district_fc")) |>
+  filter(term %in% c("(Intercept)", "year", "district_is", "district_fc")) |>
   mutate(
@@
 
-knitr::kable(d_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c"))
+knitr::kable(d_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c", "c"))
 ```
+Model estimates highlight the influence of district type on population.
+The baseline population, Chinese-administrated district population, is represented by the intercept, is estimated at 11,792,816.58, with a standard error of 18,954,543.85.
+This estimate is not a realistic estimate since the year variable is not included.
+This intercept is population at year = 0, which does not actually exist.
+Temporal impact on population is estimated using the *year* variable, observing a decline of 59,841.02 across all districts, with a standard error of 98,298.59.
+The International Settlement exhibits a population difference of -943,281.63 (standard error: 381,299.41) compared to the Chinese-administered area, while the French Concession shows a difference of -1,642,126.91 (standard error: 350,808.44).
 
-#### Historical Events
+### Historical Events
 
@@
 ```
+The effects of three historical events on population are also quantified.
+The Japanese occupation of the Chinese-administered area in 1937 (cd_occupied) is associated with an increase of 89,350.01 (standard error: 350,665.57).
+France’s surrender in 1940 (french_surrender) results in a population decrease of 735,223.28 (standard error: 340,852.1).
+The Japanese occupation of the International Settlement in 1942 (is_occupied) corresponds to a population decrease of 88,982.32 (standard error: 361,506.9).
 
-#### Historic Events' Impact on Each District
-
+### Historic Events' Impact on Each District
 ```{r}
@@
 # Filter for the specific coefficient you want (e.g., "cd_occupied")
-impact_types <- model_summary[7:12, ] |>
+impact_types <- model_summary[8:12, ] |>
   mutate(estimate = round(estimate, 2),
@@
 
-print(impact_types)
 knitr::kable(impact_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c", "c", "c", "c"))
 ```
+The interaction terms, which capture district-specific responses to historical events, provide additional insight.
+The Japanese occupation of the Chinese-administered area increases the population in the International Settlement by 89,430.69 (standard error: 414,726.8) and in the French Concession by 38,396.87 (standard error: 410,271.2).
+France’s surrender increases the population in the International Settlement by 470,617.65 (standard error: 352,215.9) and in the French Concession by 1,044,470.54 (standard error: 352,469.9).
+The Japanese occupation of the International Settlement itself is associated with an increase of 934,059.1 (standard error: 476,934.2) in the International Settlement’s population.
+Interaction terms differ from main effects by isolating the impact of historical events within each district type, providing a detailed analysis of population dynamics during this period.
 

### 2024-12-03 paper/paper.qmd
added to appendix model testing

@@
 
-## Overview
-
 Data is cleaned and analyzed using the open-source statistical programming language R [@citeR] and supporting packages including tidyverse [@tidyverse], arrow [@arrow], readr [@readr], knitr [@knitr], kableExtra [@kableExtra], modelsummary [@modelsummary], rstanarm [@rstanarm], dplyr [@dplyr], and broom.mixed [@broom.mixed].
@@
 
--   talk about where the data in my primary reference book is gathered
--   mentions the credibility of source and instability of recording instrument & methodology
+The primary dataset is sourced from the appendix of the research publication 《旧上海人口变迁的研究》 (@sh), which includes selected excerpts from historical government census records.
+Due to the age of the original census documents, they are no longer available online.
+To address gaps in the primary dataset, complementary data was obtained from the research platform Virtual Shanghai (@virtualshanghai), providing crucial insights to fill missing areas.
 
@@
 
-Place: Shanghai, China
+Between 1936 and 1942, China was in a state of political and social upheaval, marked by increasing Japanese aggression and internal instability.
+Shanghai, a critical urban center, was divided into three districts: the Chinese-administered district, the International Settlement (primarily governed by the U.K.
+and U.S.), and the French Concession (under French governance).
+The International Settlement and French Concession operated with significant autonomy compared to the Chinese government’s limited authority over its district.
+Each district occupied distinct proportions of Shanghai’s urban landscape.
 
-When: 1936-1942
-
-Who: Chinese population in Shanghai
-
-Define: 1.
-give 1-2 sentence broad overview of China's state of unrest 2.THREE districts in Shanghai: Chinese District, International Settlement, French Concession - who controlled each district and the level of governance each authority have in comparison to Chinese government 3.Outline area (%) of each district (do not get into specifics, put that in Results section)
-
-Important Event Timeline
+**Reference Timeline**:
 
@@
 
--   how population is recorded
--   Why choose 1936 - 1942 (ex. if an event occurred in Nov of 1937, would I take values of 1937 as a variable for prior to event occurrence or after?)
+The majority of the data used in this analysis were collected by police officers or hired local authorities within each district of Shanghai, as detailed in the source (@sh, page 2).
 
-Survey Difficulties - Population Volatility caused by Warfare: Population is extreme volatile within this time period, population shifts constantly as 战况 proceed - Regional Recording Limitations: Survey response collect difficulty varies between districts.
-- Resistance due to Political Risk
+This paper focuses on population data from 1936 to 1942, a timeframe determined by both historical relevance and data availability.
+The analysis centers on the impact of three major historical events, beginning with the Japanese occupation of the Chinese-administered district on November 12, 1937.
+Given that Japanese forces first entered Shanghai on August 13, 1937, the year 1936 is chosen as the baseline or “no-treatment” year for comparison.
+The analysis concludes with the year 1942, as district-specific population data after this year is unavailable.
+The lack of records for the period between 1943 and 1949 coincides with the political transition to the People’s Republic of China, making 1942 the final year for which reliable district-based population data exists.
+
+The survey process faced several challenges, primarily due to population volatility caused by wartime conditions.
+Population shifts were frequent and unpredictable as military conflicts unfolded.
+Additionally, survey efforts encountered varying degrees of difficulty across districts due to logistical and political constraints.
+Resistance from the local population, often rooted in political risks, further complicated data collection efforts.
+These challenges underline the complexities of accurately recording population dynamics during a period of significant unrest and upheaval.
 
@@
 ```
+This paper primarily evaluates three historic events between 1936 - 1942:
+1. The Japanese occupation of Shanghai's Chinese-administrated District -- 1937-11-12
+2. France surrendered to Germany -- 1940-06-22
+3. Japanese armed forces claims authority over International Settlement -- 1942-01
+
+The first and third events should have very straight-forward consequences on population.
+The shifting over governing power to a foreign, hostile country would intuitive cause local population to panick and evacuate.
+In this paper, we initially assumed that Japanese occupation would decrease population in the corresponding area.
+
+The effect of the second event is less direct.
+In 1940, European battlefield is still filled with WWII soldiers.
+When France surrendered to Germany in June, Japan -- an ally of Germany, accepted France's new status as mutural German allies.
+The Japanese forces chose to stay out of the French Concession District in Shanghai.
+(@video) The French Concession remained un-conquered until the Japanese withdrew from Shanghai in 1945.
 
@@
 
--   outcome variable is *population*
+The outcome variable in this analysis is the *population* from 1936 to 1942.
+
+District-level population data is missing for the years 1938, 1939, 1940 (partially), and 1941 in the government records.
+For 1938, 1939, and 1940, the population counts for all districts are unavailable due to undocumented reasons.
+To estimate these values, the population for the International Settlement and French Concession is deduced by adding the refugee population in their camps to their respective 1937 population counts.
+The population of the Chinese-administered district is then estimated by subtracting the total number of refugees in the two foreign districts from its 1937 population.
+
+The missing population data for 1941 is estimated by calibrating the pre-established 1942 population dataset (@population1941) against the primary data.
+A multiplier is derived to adjust the 1941 data to align as closely as possible with the available records, providing an approximate but consistent estimation.
+
+```{r}
+#| echo: false
+#| eval: true
+#| label: tbl-pop
+#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| warning: false
+#| message: false
+
+knitr::kable(combined_data, 
+             col.names = c("Year", "Chinese-administered Population", "International Settlement Population", "French Concession Population"), 
+             align = c("c", "c", "c", "c"), 
+             caption = "Population by District and Year (1936-1942)")
+
+```
 
@@
 
-The interaction terms in the model are essential because they capture how the impact of historical events (e.g., the 1937 occupation of Chinese-administered districts, the 1940 refugee rejection in the French Concession, and the 1942 occupation of the International Settlement) varies across different district types.
-By including interactions between event indicators and district types, the model accounts for district-specific responses to each event, controlling for the fact that the effect of an event on population changes may not be uniform across all districts.
-For instance, the 1937 occupation might lead to population declines in Chinese-administered districts but population increases in the International Settlement due to refugee influx.
-These terms ensure that the model can differentiate and estimate the unique effects of each event within each district type, thereby improving precision and interpretability.
-
 -   *district_is × cd_occupied*: Captures the effect of the 1937 occupation on the International Settlement in comparison to the Chinese-administered district (base district).
@@
 ### Model justification
+The Difference-in-Difference model is chosen to evaluate the impact of historical events by comparing the observed outcomes, population changes, to an imaginary counterfactual scenario where these events did not occur.
+The year variable captures the temporal trends, allowing the model to account for changes in population over time.
+The district variable identifies the three distinct regions in Shanghai (Chinese-administered district, International Settlement, and French Concession), each subject to unique governance and historical impacts.
+These inclusions enable the model to control for factors beyond the primary variables of interest (historical events).
 
-We expect a positive relationship between the size of the wings and time spent aloft. In particular...
+The interaction terms in the model are essential because they capture how the impact of historical events (e.g., the 1937 occupation of Chinese-administered districts, the 1940 refugee rejection in the French Concession, and the 1942 occupation of the International Settlement) varies across different district types.
+By including interactions between event indicators and district types, the model accounts for district-specific responses to each event, controlling for the fact that the effect of an event on population changes may not be uniform across all districts.
+For instance, the 1937 occupation might lead to population declines in Chinese-administered districts but population increases in the International Settlement due to refugee influx.
+These terms ensure that the model can differentiate and estimate the unique effects of each event within each district type, thereby improving precision and interpretability.
 
-We can use maths by including latex between dollar signs, for instance $\theta$.
+A negative relationship is expected between year and population because the period under study (1936–1942) was marked by military conflict and foreign occupation, creating an unstable living environment.
+Specifically:
+- Chinese-administered District: A population decline is expected due to the Japanese occupation in 1937.
+- French Concession: A population decrease is anticipated following France’s surrender in 1940, which led to refugee rejection.
+- International Settlement: A population decline is expected after its occupation by Japanese forces in 1942.
 
@@
 ## Population Trend
-
 ```{r}
@@
 ## Interpretation of the Event Impacts
+The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts.
+In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession.
+Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself.
 
 ### Impact of Occupation in Chinese District
+- By intuition, we would think that the foreign-force occupation of a district would lead to its population to fled to other areas.
+However, this does not seem the case for the Chinese-administrated District within Shanghai.
+- This counter-intuitive phenomenon might be caused by several factors. 
+Firstly, the increase in the districts population might be cause by an influx of foreign state refugees.
+Shanghai was, and still is, one of the largest economic center in China and has an abundance of non-land-dependent job opportunity.
+战争时期，随时随地可能发生的战事极大的interrupted agriculture, subsequently leading to a large volume of unemployed farmers.
+These unemployed population will likely flood to economic centers and industrial center in search of a new job.
+(@sh, page 14)
 
@@
 
-# Additional data details
-
 # Model details {#sec-model-details}
-
 ## Model Summary Table
@@
 #| eval: true
-#| warning: false
-#| message: false
-
-library(rstanarm)
-
-did_model <-
-  readRDS(file = here::here("models/did_model.rds"))
-```
-
-```{r}
-#| echo: false
-#| eval: true
 #| label: tbl-modelresults
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
+#| tbl-cap: "Complete Model Summary for DiD model used in analysis"
 #| warning: false
@@
 ```
+\newpage
 
@@
 
-In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. This shows...
+In @fig-ppcheckandposteriorvsprior-1 we implement a posterior predictive check. 
+The posterior predictive check evaluates how well the model-generated predictions ($y_{rep}$) match the observed data ($y$).
+The overlay of the predictive distribution with the observed data indicates that the model captures the general trends and variability in the data.
+The similarity between the observed data and the model’s predictions suggests that the model provides a good fit for the observed population data.
 
-In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. This shows...
+In @fig-ppcheckandposteriorvsprior-2 we compare the posterior with the prior. 
+The comparison between the posterior and prior distributions shows how the data influences the model parameters.
+The posterior distributions are narrower and more distinct compared to the priors, indicating that the data strongly informed the parameter estimates.
+Parameters like $cd\_occupied$ and $district\_fc$ show clear shifts in their posterior means, signifying their significant role in explaining population changes.
+Conversely, parameters with less distinct posteriors might indicate weaker evidence from the data.
 
@@
 
-@fig-stanareyouokay-1 is a trace plot. It shows... This suggests...
+@fig-stanareyouokay-1 is a trace plot.
+The trace plot displays the MCMC sampling for each parameter across the chains.
+The chains appear to mix well, with no clear trends or patterns, indicating that the algorithm explores the parameter space efficiently.
+This suggests good convergence, as the chains reach their stationary distribution without being stuck in local modes.
 
-@fig-stanareyouokay-2 is a Rhat plot. It shows... This suggests...
+@fig-stanareyouokay-2 is a Rhat plot.
+The Rhat plot evaluates the convergence of the chains by comparing the within-chain and between-chain variance.
+All Rhat values are close to 1.0, indicating that the chains have converged.
+This suggests that the parameter estimates are reliable, and the sampling process provides consistent results across chains.
 

### 2024-12-03 other/datasheet/datasheet.qmd
refined discussion section, added visualization

---
title: "Datasheet for 'model_format'"
author: 
  - Sandy Yu
thanks: "Code and data are available at: https://github.com/Jingying-yu/Shanghai_population_change"
date: today
date-format: long
format: pdf
bibliography: data_ref.bib
---

Extract of the questions from @gebru2021datasheets.

**Motivation**

1. *For what purpose was the dataset created? Was there a specific task in mind? Was there a specific gap that needed to be filled? Please provide a description.*
    - The dataset was created to enable analysis on factors affecting population change in Shanghai during 1936 - 1942. I was unable to find a publicly available dataset in a structured format that had the the necessary district-base population information duing this exmining period that was needed for modelling.
2. *Who created the dataset (for example, which team, research group) and on behalf of which entity (for example, company, institution, organization)?*
    - Sandy Yu, while studying at the University of Toronto as an undergraduate student.
3. *Who funded the creation of the dataset? If there is an associated grant, please provide the name of the grantor and the grant name and number.*
    - No funding was received for this project.
4. *Any other comments?*
    - N.A.

**Composition**

1. *What do the instances that comprise the dataset represent (for example, documents, photos, people, countries)? Are there multiple types of instances (for example, movies, users, and ratings; people and interactions between them; nodes and edges)? Please provide a description.*
	- Each row of the dataset is contains the year, district type, population (within the specific district), and a few binary variable that indicate event occurance and district identity.
2. *How many instances are there in total (of each type, if appropriate)?*
	- 21 rows have been recorded
3. *Does the dataset contain all possible instances or is it a sample (not necessarily random) of instances from a larger set? If the dataset is a sample, then what is the larger set? Is the sample representative of the larger set (for example, geographic coverage)? If so, please describe how this representativeness was validated/verified. If it is not representative of the larger set, please describe why not (for example, to cover a more diverse range of instances, because instances were withheld or unavailable).*
	- No this dataset is a sample of an entire census. Primary dataset used to compose the final dataset contains district-based population data from 1852 to 1950. Only section of the primary dataset is taken for the final dataset. This choice was made because the paper only focus on analyzing data during the period of 1936-1942. THis time range is when the 3 historic events of interest occurred.
4. *What data does each instance consist of? "Raw" data (for example, unprocessed text or images) or features? In either case, please provide a description.*
	- Each instance consists of the respective year, district type, population and binary indicators detailed above.
5. *Is there a label or target associated with each instance? If so, please provide a description.*
	- Yes, the year variable coupled with the district type variable are unique identifier for each instance.
6. *Is any information missing from individual instances? If so, please provide a description, explaining why this information is missing (for example, because it was unavailable). This does not include intentionally removed information, but might include, for example, redacted text.*
	- The primary dataset have a few population observation missing, they are filled using estimates from complementary datasets found on Virtual Shanghai Platform (@virtualshanghai)
7. *Are relationships between individual instances made explicit (for example, users' movie ratings, social network links)? If so, please describe how these relationships are made explicit.*
	- Yes, through the unique year + district type combination. Population observation is recorded once for a district type every year in the dataset.
8. *Are there recommended data splits (for example, training, development/validation, testing)? If so, please provide a description of these splits, explaining the rationale behind them.*
	- No
9. *Are there any errors, sources of noise, or redundancies in the dataset? If so, please provide a description.*
	- Yes, data was missing for 1938, 1939, 1940 (partial), and 1941 in the primary dataset. The information in the primary dataset was the most reliable since it was gathered by government census. The complementary datasets used to fill in the blanks are estimates of the real data which could cause trouble. (Please see data section in the paper for method of population estimation)
10. *Is the dataset self-contained, or does it link to or otherwise rely on external resources (for example, websites, tweets, other datasets)? If it links to or relies on external resources, a) are there guarantees that they will exist, and remain constant, over time; b) are there official archival versions of the complete dataset (that is, including the external resources as they existed at the time the dataset was created); c) are there any restrictions (for example, licenses, fees) associated with any of the external resources that might apply to a dataset consumer? Please provide descriptions of all external resources and any restrictions associated with them, as well as links or other access points, as appropriate.*
	- Self-contained
11. *Does the dataset contain data that might be considered confidential (for example, data that is protected by legal privilege or by doctor-patient confidentiality, data that includes the content of individuals' non-public communications)? If so, please provide a description.*
	- No, all data were gathered from public sources.
12. *Does the dataset contain data that, if viewed directly, might be offensive, insulting, threatening, or might otherwise cause anxiety? If so, please describe why.*
	- No
13. *Does the dataset identify any sub-populations (for example, by age, gender)? If so, please describe how these subpopulations are identified and provide a description of their respective distributions within the dataset.*
	- Population is divided into district types
14. *Is it possible to identify individuals (that is, one or more natural persons), either directly or indirectly (that is, in combination with other data) from the dataset? If so, please describe how.*
	- The dataset does not concern any individual.
15. *Does the dataset contain data that might be considered sensitive in any way (for example, data that reveals race or ethnic origins, sexual orientations, religious beliefs, political opinions or union memberships, or locations; financial or health data; biometric or genetic data; forms of government identification, such as social security numbers; criminal history)? If so, please provide a description.*
	- No
16. *Any other comments?*
	- No

**Collection process**

1. *How was the data associated with each instance acquired? Was the data directly observable (for example, raw text, movie ratings), reported by subjects (for example, survey responses), or indirectly inferred/derived from other data (for example, part-of-speech tags, model-based guesses for age or language)? If the data was reported by subjects or indirectly inferred/derived from other data, was the data validated/verified? If so, please describe how.*
	- Primary dataset (shanghai_population_1852_1950) was found in the appendix of a 1980 research publication on the population shift in Shanghai (@sh). The data source was government census in the 1982-1950.
	- complementary datasets (refugees_data & 1941_42) are gathered on the research platform @virtualshanghai.
2. *What mechanisms or procedures were used to collect the data (for example, hardware apparatuses or sensors, manual human curation, software programs, software APIs)? How were these mechanisms or procedures validated?*
	- Electronic version of the primary dataset data table is scanned using ChatGPT 4o and converted to Excel
	- complementary datasets (refugees_data & 1941_42) are gathered on the research platform @virtualshanghai and downloaded using open source statistical programming language R (@citeR).
3. *If the dataset is a sample from a larger set, what was the sampling strategy (for example, deterministic, probabilistic with specific sampling probabilities)?*
	- Dataset is a subset of population records published by government official, taking only the time range of interest.
4. *Who was involved in the data collection process (for example, students, crowdworkers, contractors) and how were they compensated (for example, how much were crowdworkers paid)?*
	- myself (Sandy Yu)
5. *Over what timeframe was the data collected? Does this timeframe match the creation timeframe of the data associated with the instances (for example, recent crawl of old news articles)? If not, please describe the timeframe in which the data associated with the instances was created.*
	- Data was collected and put-together in Novemeber - December of 2024
6. *Were any ethical review processes conducted (for example, by an institutional review board)? If so, please provide a description of these review processes, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
7. *Did you collect the data from the individuals in question directly, or obtain it via third parties or other sources (for example, websites)?*
	- No, all the data are open-sourced
8. *Were the individuals in question notified about the data collection? If so, please describe (or show with screenshots or other information) how notice was provided, and provide a link or other access point to, or otherwise reproduce, the exact language of the notification itself.*
	- NA
9. *Did the individuals in question consent to the collection and use of their data? If so, please describe (or show with screenshots or other information) how consent was requested and provided, and provide a link or other access point to, or otherwise reproduce, the exact language to which the individuals consented.*
	- NA
10. *If consent was obtained, were the consenting individuals provided with a mechanism to revoke their consent in the future or for certain uses? If so, please provide a description, as well as a link or other access point to the mechanism (if appropriate).*
	- NA
11. *Has an analysis of the potential impact of the dataset and its use on data subjects (for example, a data protection impact analysis) been conducted? If so, please provide a description of this analysis, including the outcomes, as well as a link or other access point to any supporting documentation.*
	- No
12. *Any other comments?*
	- No

**Preprocessing/cleaning/labeling**

1.  *Was any preprocessing/cleaning/labeling of the data done (for example, discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instances, processing of missing values)? If so, please provide a description. If not, you may skip the remaining questions in this section.*
  - Yes cleaning of the data was done.
2.  *Was the "raw" data saved in addition to the preprocessed/cleaned/labeled data (for example, to support unanticipated future uses)? If so, please provide a link or other access point to the "raw" data.*
  - Yes
3.  *Is the software that was used to preprocess/clean/label the data available? If so, please provide a link or other access point.*
  - R and Excel were used
4.  *Any other comments?*
  - No

**Uses**

1. *Has the dataset been used for any tasks already? If so, please provide a description.*
	- No, the dataset is specifically put together for this paper.
2. *Is there a repository that links to any or all papers or systems that use the dataset? If so, please provide a link or other access point.*
	- No
3. *What (other) tasks could the dataset be used for?*
	- Potentially, but none I can think of right now
4. *Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses? For example, is there anything that a dataset consumer might need to know to avoid uses that could result in unfair treatment of individuals or groups (for example, stereotyping, quality of service issues) or other risks or harms (for example, legal risks, financial harms)? If so, please provide a description. Is there anything a dataset consumer could do to mitigate these risks or harms?*
	- No
5. *Are there tasks for which the dataset should not be used? If so, please provide a description.*
	- No
6. *Any other comments?*
	- No

**Distribution**

1.  *Will the dataset be distributed to third parties outside of the entity (for example, company, institution, organization) on behalf of which the dataset was created? If so, please provide a description.*
  - No
2.  *How will the dataset be distributed (for example, tarball on website, API, GitHub)? Does the dataset have a digital object identifier (DOI)?*
  - Data will be available on Github
3.  *When will the dataset be distributed?*
  - data is available now
4.  *Will the dataset be distributed under a copyright or other intellectual property (IP) license, and/or under applicable terms of use (ToU)? If so, please describe this license and/ or ToU, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms or ToU, as well as any fees associated with these restrictions.*
  - No.
5.  *Have any third parties imposed IP-based or other restrictions on the data associated with the instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any relevant licensing terms, as well as any fees associated with these restrictions.*
  - None that are known
6.  *Do any export controls or other regulatory restrictions apply to the dataset or to individual instances? If so, please describe these restrictions, and provide a link or other access point to, or otherwise reproduce, any supporting documentation.*
  - None that are known
7.  *Any other comments?*
  - No

**Maintenance**

1.  *Who will be supporting/hosting/maintaining the dataset?*
  - Sandy Yu
2.  *How can the owner/curator/manager of the dataset be contacted (for example, email address)?*
  - jingying.yu@mail.utoronto.ca
3.  *Is there an erratum? If so, please provide a link or other access point.*
  - No, the dataset is just updated.
4.  *Will the dataset be updated (for example, to correct labeling errors, add new instances, delete instances)? If so, please describe how often, by whom, and how updates will be communicated to dataset consumers (for example, mailing list, GitHub)?*
  - Unlikely
5.  *If the dataset relates to people, are there applicable limits on the retention of the data associated with the instances (for example, were the individuals in question told that their data would be retained for a fixed period of time and then deleted)? If so, please describe these limits and explain how they will be enforced.*
  - Not applicable
6.  *Will older versions of the dataset continue to be supported/hosted/maintained? If so, please describe how. If not, please describe how its obsolescence will be communicated to dataset consumers.*
  - The updated dataset is the first version and likely the last
7.  *If others want to extend/augment/build on/contribute to the dataset, is there a mechanism for them to do so? If so, please provide a description. Will these contributions be validated/verified? If so, please describe how. If not, why not? Is there a process for communicating/distributing these contributions to dataset consumers? If so, please provide a description.*
  - Pull request on GitHub.
8.  *Any other comments?*
  - No

\newpage

# References

### 2024-12-03 paper/paper.qmd
refined discussion section, added visualization

@@
 number-sections: true
+toc: true
 bibliography: references.bib
@@
 
-1940-06-22: France surrendered to Germany --\> French Concession stopped taking refugees
+3\. 1940-06-22: France surrendered to Germany --\> French Concession stopped taking refugees
 
-3\. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)
+4\. 1942-01: Japanese armed forces claims authority over International Settlement (which was mainly under the governance of U.K and U.S prior to this date)
 
-4\. 1945-08-15: Japan surrendered in WWII
+5\. 1945-08-15: Japan surrendered in WWII
 
-5\. 1945-10: most Japanese armed forces withdrew from Shanghai
+6\. 1945-10: most Japanese armed forces withdrew from Shanghai
 
@@
 ```
-This paper primarily evaluates three historic events between 1936 - 1942:
-1. The Japanese occupation of Shanghai's Chinese-administrated District -- 1937-11-12
-2. France surrendered to Germany -- 1940-06-22
-3. Japanese armed forces claims authority over International Settlement -- 1942-01
+
+This paper primarily evaluates three historic events between 1936 - 1942: 1.
+The Japanese occupation of Shanghai's Chinese-administrated District -- 1937-11-12 2.
+France surrendered to Germany -- 1940-06-22 3.
+Japanese armed forces claims authority over International Settlement -- 1942-01
 
@@
 
-# Model
+# Model {#sec-model}
 
@@
 
-$$\mu_i = \alpha + \beta_k$$
-$$\alpha \sim \text{Normal}(0, 2.5)$$
+$$\mu_i = \alpha + \beta_k$$ $$\alpha \sim \text{Normal}(0, 2.5)$$
 
@@
 ### Model justification
+
 The Difference-in-Difference model is chosen to evaluate the impact of historical events by comparing the observed outcomes, population changes, to an imaginary counterfactual scenario where these events did not occur.
@@
 A negative relationship is expected between year and population because the period under study (1936–1942) was marked by military conflict and foreign occupation, creating an unstable living environment.
-Specifically:
-- Chinese-administered District: A population decline is expected due to the Japanese occupation in 1937.
+Specifically: - Chinese-administered District: A population decline is expected due to the Japanese occupation in 1937.
 - French Concession: A population decrease is anticipated following France’s surrender in 1940, which led to refugee rejection.
@@
 
-# Results
+# Results {#sec-results}
+
 This section presents the population trends in Shanghai’s districts between 1936 and 1942, the estimated effects of district type and key historical events on population, and the district-specific impacts of these events as captured by interaction terms.
@@
 ## Population Trend
-```{r}
+
+```{r, fig.pos="H"}
 #| label: fig-pop
@@
     legend.position = "bottom",
-    text = element_text(size = 12),
+    text = element_text(size = 10),
     plot.title = element_text(hjust = 0.5)
@@
 ```
+
 The population trends from 1936 to 1942 reveal distinct shifts across the three districts in Shanghai: the Chinese-administered area, the French Concession, and the International Settlement.
@@
 ```
+
 Model estimates highlight the influence of district type on population.
@@
 ```
+
 The effects of three historical events on population are also quantified.
@@
 ### Historic Events' Impact on Each District
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-events_district
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
 
-# Filter for the specific coefficient you want (e.g., "cd_occupied")
-impact_types <- model_summary[8:12, ] |>
-  mutate(estimate = round(estimate, 2),
-    std.error = round(std.error, 2))
-
-knitr::kable(impact_types, col.names = c("Parameters", "Estimated Effect", "Standard Error"), align = c("c", "c", "c", "c", "c", "c"))
-```
 The interaction terms, which capture district-specific responses to historical events, provide additional insight.
@@
 
-# Discussion
+```{r, fig.pos="H"}
+#| label: fig-cd_occupied
+#| fig-cap: Trend of Population after Chinese-administrated District became occupied in 1937
+#| echo: false
+#| warning: false
+#| message: false
 
-## Interpretation of the Event Impacts
-The results indicate that the Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts.
-In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession.
+ggplot(model_format, aes(x = year, y = population, fill = district_type)) +
+  geom_bar(stat = "identity") +  # Bar plot
+  facet_wrap(~ district_type, strip.position = "bottom") +  # Facet by district_type
+  geom_vline(xintercept = 1937, linetype = "dashed", color = "red") +  # Vertical dashed line
+  geom_label(
+    aes(
+      x = 1939, y = 2500000,  # Adjust text position above 2,500,000
+      label = "Starting from 1937,\nCHN District is occupied ---->"
+    ),
+    inherit.aes = FALSE,  # Prevent inheritance from aes()
+    fill = "pink", color = "red", alpha = 0.3, size = 2.5, label.size = 0
+  ) +
+  # Add trend line for years >= 1937
+  geom_smooth(
+    data = model_format[model_format$year >= 1937, ],  # Filter data for years >= 1937
+    aes(group = district_type),
+    alpha = 0.8,
+    method = "lm",  # Linear regression
+    linetype = "dotted",
+    color = "black", size = 1, se = FALSE  # Black trend line, no standard error
+  ) +
+  scale_y_continuous(limits = c(0, 2800000)) +  # Set y-axis limit to 2,800,000
+  labs(
+    title = "Population Trends after Occupation of CHN District",
+    x = "Year",
+    y = "Population",
+    fill = "Year"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
+    legend.position = "bottom"
+  )
+```
+
+```{r, fig.pos="H"}
+#| label: fig-fr_surrender
+#| fig-cap: Visualization of Population trend after French surrender in 1940
+#| echo: false
+#| warning: false
+#| message: false
+
+ggplot(model_format, aes(x = year, y = population, fill = district_type)) +
+  geom_bar(stat = "identity") +  # Bar plot
+  facet_wrap(~ district_type, strip.position = "bottom") +  # Facet by district_type
+  geom_vline(xintercept = 1940, linetype = "dashed", color = "red") +  # Vertical dashed line
+  geom_label(
+    aes(
+      x = 1939, y = 2500000,  # Adjust text position above 2,500,000
+      label = "Starting from 1940, \nFrance surrendered to Germany -->"
+    ),
+    inherit.aes = FALSE,  # Prevent inheritance from aes()
+    fill = "lightgreen", color = "black", alpha = 0.3, size = 2, label.size = 0
+  ) +
+  # Add trend line for years >= 1937
+  geom_smooth(
+    data = model_format[model_format$year >= 1940, ],  # Filter data for years >= 1937
+    aes(group = district_type),
+    alpha = 0.8,
+    method = "lm",  # Linear regression
+    linetype = "dotted",
+    color = "black", size = 1, se = FALSE  # Black trend line, no standard error
+  ) +
+  scale_y_continuous(limits = c(0, 2800000)) +  # Set y-axis limit to 2,800,000
+  labs(
+    title = "Population Trend After French Surrender",
+    x = "Year",
+    y = "Population",
+    fill = "Year"
+  ) +
+  theme_minimal() +
+  theme(
+    plot.title = element_text(hjust = 0.5, size = 14, face = "bold"),
+    legend.position = "bottom"
+  )
+```
+
+# Discussion {#sec-discussion}
+
+The results highlight the varying population shifts in Shanghai’s three districts during key historical events in WWII.
+The Japanese occupation of the Chinese-administered district led to an overall increase in Shanghai’s population across all districts.
+In contrast, France’s surrender during WWII negatively impacted population numbers in all districts except the French Concession.
 Similarly, the Japanese occupation of the International Settlement caused population declines in all districts except the International Settlement itself.
 
-### Impact of Occupation in Chinese District
-- By intuition, we would think that the foreign-force occupation of a district would lead to its population to fled to other areas.
-However, this does not seem the case for the Chinese-administrated District within Shanghai.
-- This counter-intuitive phenomenon might be caused by several factors. 
-Firstly, the increase in the districts population might be cause by an influx of foreign state refugees.
-Shanghai was, and still is, one of the largest economic center in China and has an abundance of non-land-dependent job opportunity.
-战争时期，随时随地可能发生的战事极大的interrupted agriculture, subsequently leading to a large volume of unemployed farmers.
-These unemployed population will likely flood to economic centers and industrial center in search of a new job.
-(@sh, page 14)
+## Occupation in Chinese District
 
-### Impact of French Surrendering to Germany on Shanghai
+Contrary to expectations, the Japanese occupation of the Chinese-administered district did not result in population declines.
+Instead, this district experienced an increase in population, likely driven by refugees fleeing rural provinces.
+The devastation of agricultural economies due to ongoing warfare forced farmers to seek alternative livelihoods in urban centers.
+Shanghai, being an economic hub with abundant industrial job opportunities, became a natural destination for displaced populations (@sh, page 14).
 
-### Impact of Occupation in International Settlement
+Industrialization during the 1930s and 1940s was concentrated in cities like Shanghai, while most provinces remained predominantly rural.
+Disrupted farming activities caused widespread unemployment, prompting many to migrate to Shanghai, where income was not tied to land productivity.
+The high population density in Shanghai further fueled its economic growth, offering a range of job opportunities, especially in manufacturing industries located in the foreign settlements.
 
-## Reason why the French Concession was Exempted from Japanese Occupation
+However, access to jobs was not uniform.
+Historical records suggest that certain industries were dominated by migrants from specific provinces due to the strong influence of regional associations.
+For example, hotel businesses were often monopolized by individuals from Hunan, while the footbath service industry was controlled by migrants from Northern Jiangsu.
+This social network-based hiring created barriers to entry for outsiders, shaping the employment landscape in Shanghai.
 
--   During WWII, on the European battlefield, France surrendered to Germany on June 22nd of 1940 (Check this & reference with a credible source).
-Since Japan was on the same side as Germany during that time, Japanese armed forces decided allow the French Concession to retain its own governance.
--   However, the French Concession is still constantly under the watch of the Japanese forces that has occupied the rest of Shanghai since 1942.
-街上不得有侮辱日本的旗帜或者宣言，官方必须积极配合日本统治者进行有利于日本统治的宣传,etc.(can reference to video summary here)
+## French Surrendering to Germany on Shanghai Population
 
-## Refugees from outside of Shanghai Province
+The French Concession displayed unique population dynamics during WWII.
+Following France’s surrender to Germany on June 22, 1940, the concession ceased accepting refugees.
+This sudden shift in refugee policy aligns with geopolitical developments, as France temporarily allied with Germany during this period.
+The Japanese armed forces allowed the French Concession to maintain governance autonomy, likely due to this alliance.
 
--   industrialization was not so popular back in the 1930s, many provinces are still mostly rural.
-But warfare messed with the land and the yields, causing many farmers to starve and ultimately have to seek refugee (find job) in industrialized city (where income is not dependent on land yield)
--   many people flooded to Shanghai for this reason (can insert calculation in data table 20 from reference book here)
+Despite retaining governance, the French Concession operated under the watchful eye of Japanese forces, who occupied the rest of Shanghai by 1942.
+Compliance with Japanese regulations, including bans on anti-Japanese propaganda, was mandatory.
+The political alignment with Germany thus shielded the French Concession from direct occupation but altered its role as a haven for refugees.
 
-### Job Oppurtunities in Shanghai
-
-Aside from the instability caused by the Japanese armed forces, there are a few other reasons for Chinese population to move into the international settlement & French Concession.
-1.
-Job opportunities - Heart of Shanghai city in the 1930-1940s, high pop density lead to boom of economy = more job opportunities - many factories are located with the settlements (less so in concession)
-
-### Barrier to Entry in Job Market
-
-2.  Barrier to Entry for certain job types
-
--   旧时候 -- 通讯还没有那么发达的时候，人们都很团结。那个时候同乡会的力量很强大。在外省，从同一个省来的漂泊者会互相帮扶着垄断一个城市的某种行业。例如，在旧上海，要做酒店生意的话你就必须是湖南人，给人做洗脚生意的肯定是苏北人。。。
+## Occupation in International Settlement
+The Japanese occupation of the International Settlement resulted in a population pattern contrary to initial expectations.
+While occupation typically drives residents away, the settlement remained one of the safest and most expensive areas in Shanghai.
+With the French Concession no longer accepting refugees, the International Settlement became the primary refuge for displaced individuals, stabilizing its population despite foreign control.
+Its status as an elite residential district further insulated it from severe population declines.
 
@@
 
--   after the Japanese armed forces withdrawed from Shanghai, what follows is not recovery and rest for the local population
--   Competition for power within China's 2 political parties caused full-scale political warfare, now known as the *Chinese Civil War*
--   unlike Western political parties, Chinese political parties in the 1900s are more like parties of a throne.
-They each have their own ideology and an armed forces that follow.
-Most of all of the provinces are effected by this internal warfare, which ended in 1949 as 国民党 lost and withdrawed to Taiwan.
+The end of Japanese occupation in 1945 did not bring stability to Shanghai.
+Instead, the city became embroiled in the Chinese Civil War, as the two dominant political parties—Kuomintang and the Chinese Communist Party—vied for control.
+Unlike Western political parties, these factions operated as militarized entities with distinct ideologies and armed forces.
+The civil war, which engulfed much of China, ended in 1949 with the Kuomintang retreating to Taiwan, leaving behind a landscape marked by prolonged instability.
 
@@
 
-### Data Measurement Weaknesses
+The study acknowledges several limitations.
+First, data recorded during wartime is incomplete, with many population figures missing.
+Additionally, population counts were based on households, with the number of individuals per household estimated from historical averages.
+This approach may not accurately capture the actual population.
+Furthermore, under-reporting or partial reporting for economic or convenience reasons may have compromised data accuracy.
 
--   data was recorded during wartime, many numbers were missing
--   base unit for population records is not ppl, it is instead "household". \# of ppl in a household is estimated based on historical data
--   many people chose to not report or partially report numbers due to convience or economic reasons, data may not be accurate
-
-### Next Steps
+Future research should focus on improving data reconstruction methods, incorporating archival records, and leveraging advanced modeling techniques to address these limitations.
+Expanding the analysis to include other affected regions in China could also provide a broader understanding of the population dynamics during WWII.
 
@@
 # Model details {#sec-model-details}
-## Model Summary Table
-
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-modelresults
-#| tbl-cap: "Complete Model Summary for DiD model used in analysis"
-#| warning: false
-
-modelsummary::modelsummary(
-  list(
-    "Population model" = did_model
-  ),
-  statistic = "mad",
-  fmt = 2,
-  metrics = c("R2", "RMSE")
-)
-```
-\newpage
 
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| eval: true
@@
 
-```{r}
+```{r, fig.pos="H"}
 #| echo: false
@@
 
+## Model Summary
+```{r, fig.pos="H"}
+#| echo: false
+#| eval: true
+#| label: tbl-modelresults
+#| tbl-cap: "Complete Model Summary for DiD model used in analysis"
+#| warning: false
+
+modelsummary::modelsummary(
+  list(
+    "Population model" = did_model
+  ),
+  statistic = "mad",
+  fmt = 2,
+  metrics = c("R2", "RMSE")
+)
+
+```
 \newpage
@@
 
-This appendix presents an idealized design for a population sampling survey, assuming that a data-recorder has unlimited time and authority to collect data within the historical timeframe of 1936–1942.
+This appendix presents an idealized design for a population sampling survey, assuming that a data-recorder has unlimited time and authority to collect data within the historical time-frame of 1936–1942.
 The proposed methodology outlines a systematic approach to gathering detailed population data from Shanghai’s districts during pivotal wartime events, with considerations for the practical constraints and technology available during that period.

### 2024-12-04 paper/paper.qmd
added to introduction section in paper.qmd and re-rendered

@@
 
-Overview paragraph
+The 1930s-1940s were marked by extreme volatility and chaos.
+World War II devastated regions across Europe and Asia.
+On the Western front, the Allies clashed with Nazi Germany, while in the East, Japanese forces invaded China.
+This paper examines the impact of key WWII-related events on the population dynamics of Shanghai.
 
-Estimand paragraph
+The focus of this study is to evaluate how three significant historic events—the occupation of the Chinese-administered District, France’s surrender in WWII, and the occupation of the International Settlement—affected population changes within Shanghai.
 
-Results paragraph
+The Japanese occupation of the Chinese-administered area led to an overall increase in Shanghai’s population across all districts, a counterintuitive result likely driven by an influx of refugees fleeing agricultural disruptions in rural areas for industrial and economic opportunities in the city.
+In contrast, France’s surrender during WWII had a negative impact on population numbers in all districts except the French Concession, which retained relative stability due to its continued governance under French authority, albeit under Japanese surveillance.
+Similarly, the occupation of the International Settlement caused population declines in all districts except for the International Settlement itself, which remained one of the safest and most resource-secured areas in Shanghai despite the occupation.
+These findings reflect the complex interplay between governance, security, and economic opportunity in shaping population dynamics during wartime.
 
-Why it matters paragraph
+Understanding the demographic shifts caused by major historic events provides insight into the broader socio-economic and political factors at play during times of war.
+By examining these population changes, this paper highlights how external forces and governance structures shaped the resilience and migration patterns of urban populations during WWII.
+This research also underscores the importance of context-specific analyses when studying the impacts of conflict on urban demographics.
 
@@
 
-```{r}
-#| echo: false
-#| eval: true
-#| label: tbl-outcome_variable
-#| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
-#| warning: false
-#| message: false
+This paper primarily evaluates three historic events between 1936 - 1942:
 
-knitr::kable(combined_data, col.names = c("Year", "Pop CHN District", "Pop IS", "Pop FC"), align = c("c", "c", "c", "c"))
-```
+1\. The Japanese occupation of Shanghai's Chinese-administrated District -- 1937-11-12
 
-This paper primarily evaluates three historic events between 1936 - 1942: 1.
-The Japanese occupation of Shanghai's Chinese-administrated District -- 1937-11-12 2.
-France surrendered to Germany -- 1940-06-22 3.
-Japanese armed forces claims authority over International Settlement -- 1942-01
+2\. France surrendered to Germany -- 1940-06-22
+
+3\. Japanese armed forces claims authority over International Settlement -- 1942-01
 
 The first and third events should have very straight-forward consequences on population.
-The shifting over governing power to a foreign, hostile country would intuitive cause local population to panick and evacuate.
+The shifting over governing power to a foreign, hostile country would intuitive cause local population to panic and evacuate.
 In this paper, we initially assumed that Japanese occupation would decrease population in the corresponding area.
@@
 In 1940, European battlefield is still filled with WWII soldiers.
-When France surrendered to Germany in June, Japan -- an ally of Germany, accepted France's new status as mutural German allies.
+When France surrendered to Germany in June, Japan -- an ally of Germany, accepted France's new status as mutual German allies.
 The Japanese forces chose to stay out of the French Concession District in Shanghai.
@@
 
-The outcome variable in this analysis is the *population* from 1936 to 1942.
+The outcome variable in this analysis is the *population* from 1936 to 1942. @tbl-outcome contains population data for each district within the time-frame of interest.
 
@@
 #| eval: true
-#| label: tbl-pop
+#| label: tbl-outcome
 #| tbl-cap: "Explanatory models of flight time based on wing width and wing length"
@@
 
-Time variable: year Observations used in modelling and other analysis in this paper is ranged between 1936 to 1942.
-No observation is selected before 1936 as the growth pattern varies significantly from the event of our interest (Japanese occupation of Shanghai's different districts), and no value is elected beyond 1942 due to data constraints.
-No annual population records exists on a district bases beyond 1942.
-Foreign districts 解散 in 1949 as new political party came to power and the People's Republic of China was declared.
+**Time Variable: Year**
+
+The observations used for modeling and analysis in this paper range from 1936 to 1942.
+No observations prior to 1936 are included, as population growth patterns before this period differ significantly from those influenced by the events of interest, namely the Japanese occupation of Shanghai’s districts.
+Similarly, no data beyond 1942 is utilized due to data constraints, as annual district-level population records are unavailable after this year.
+The foreign districts were dissolved in 1949 following the rise to power of a new political regime and the establishment of the People’s Republic of China.
 
@@
 
-District indicators: - Variable *district_is* abd *district_fc* are two binary variable used to indicate the district identity of an observation.
+Column 3 and 4 of @tbl-d_variables contains district identity indicators used in the analysis model.
+Variable *district_is* and *district_fc* are two binary variable used to indicate the district identity of an observation.
 There are 3 possible district identity in Shanghai during 1930s-40s: Chinese-administrated District, International Settlement, and French Concession.
@@
 Due to political reasons on the Western battlefield, this district remains untouched by the Japanese forces all the way until they withdrew from Shanghai.
-The French Concesion district takes value of *district_is = 0* and *district_fc = 1* for all analysis in the paper.
+The French Concession district takes value of *district_is = 0* and *district_fc = 1* for all analysis in the paper.
 
-Historic Event indicators: - *cd_occupied*, *french_surrender*, and *is_occupied* are binary variables that mark the whether or not a major historic event that may have impacted Shanghai's population during the observation period (1936-1942) has occured yet.
+Column 5 to 7 in @tbl-d_variables are historic event indicators.
+Variables *cd_occupied*, *french_surrender*, and *is_occupied* are binary variables that mark the whether or not a major historic event that may have impacted Shanghai's population during the observation period (1936-1942) has occurred yet.
 1.
@@
 The goal of our modelling strategy is to evaluate the impact of 2 historical events in Shanghai during WWII.
-
 Here we briefly describe the Difference-in-Difference analysis model used to investigate the impact of the Japanese forces taking over the Chinese district and International Settlement in November 1937 and December 1941 on population shift between different Districts in Shanghai.
 
-Background details and diagnostics are included in Appendix [@sec-model-details].
+Background details and diagnostics are included in Appendix [@sec-model-summary].
 
@@
 
-The Difference-in-Difference model is chosen to evaluate the impact of historical events by comparing the observed outcomes, population changes, to an imaginary counterfactual scenario where these events did not occur.
+The Difference-in-Difference model is chosen to evaluate the impact of historical events by comparing the observed outcomes, population changes, to an imaginary counter-factual scenario where these events did not occur.
 The year variable captures the temporal trends, allowing the model to account for changes in population over time.
@@
 
-The population trends from 1936 to 1942 reveal distinct shifts across the three districts in Shanghai: the Chinese-administered area, the French Concession, and the International Settlement.
+@fig-pop presents distinct population trends from 1936 to 1942 across the three districts in Shanghai: the Chinese-administered area, the French Concession, and the International Settlement.
 In the Chinese-administered area, the population remained stable until 1937, after which a decline began in 1940, continuing through 1942.
@@
 
-Model estimates highlight the influence of district type on population.
+@tbl-district estimates highlight the influence of district type on population.
 The baseline population, Chinese-administrated district population, is represented by the intercept, is estimated at 11,792,816.58, with a standard error of 18,954,543.85.
@@
 
-The effects of three historical events on population are also quantified.
+The effects of three historical events on population are also quantified in @tbl-events.
 The Japanese occupation of the Chinese-administered area in 1937 (cd_occupied) is associated with an increase of 89,350.01 (standard error: 350,665.57).
@@
 
-The interaction terms, which capture district-specific responses to historical events, provide additional insight.
+The interaction terms, which capture district-specific responses to historical events, provide additional insight. @fig-cd_occupied contains the relevant section in the model summary.
+
 The Japanese occupation of the Chinese-administered area increases the population in the International Settlement by 89,430.69 (standard error: 414,726.8) and in the French Concession by 38,396.87 (standard error: 410,271.2).
@@
 Interaction terms differ from main effects by isolating the impact of historical events within each district type, providing a detailed analysis of population dynamics during this period.
+
+District-based population trend after the occurrence of events are shown in @fig-cd_occupied, @fig-fr_surrender, and @fig-pop.
 
@@
 ## Occupation in International Settlement
+
 The Japanese occupation of the International Settlement resulted in a population pattern contrary to initial expectations.
@@
 
-## Model Summary
+## Model Summary {#sec-model-summary}
+
 ```{r, fig.pos="H"}
@@
 ```
+
 \newpage
